### 2023-08-16 Preliminary Analyses/Preliminary Data Analysis.Rmd
Prelim Data Analysis - intelligibility

---
title: "Preliminary Data Analysis"
author: "Micah E. Hirsch"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This document shows the results of the preliminary data analysis for the older adult perceptual learning study. The results shown here are primarily descriptive results and data visualizations to include in a proposal document for the 2024 Motor Speech Conference. Full data analysis will be conducted at a later time.

All data processing and analysis was conducted using R Version 4.3.1

```{r, echo = F, warning = F, message = F}

# Loading in needed packages

library(tidyverse)
library(rio)
library(gt)

# Loading in cleaned dataset

pl_data <- rio::import("Cleaned_Data.csv")

```

# Descriptive Statistics

## Intelligibility Data

We first started by calculating pretest and posttest intelligibility for each listener. This was done by summing the total number of correctly-identified words and the total number of target words presented across the phrases in the pretest and posttest phases. Then, intelligibility was calculated by dividng the total number of correct words by the total number of target words and multiplying by 100. Intelligibility improvement (posttest - pretest intelligibility) was then calculated for each listener. Click "show code" to see this process in more detail.

```{r, warning = F, message = F}

# Calculating Intelligibility

intel_data <- pl_data %>%
  ## Grouping by id (i.e. each listener in the study) and testing phase (pretest, posttest)
  dplyr::group_by(id, type) %>%
  ## Calculating total number of correct words (words_c), total number of target words (words_t),
  ## pretest and posttest intelligibility for each listener (intel).
  dplyr::summarize(words_c = sum(correct_words), 
                   words_t = sum(target_number),
                   intel = (words_c/words_t)*100) %>%
  ## Removing words_c and words_t since it is no longer needed
  dplyr::select(!c(words_c, words_t)) %>%
  tidyr::pivot_wider(names_from = type,
                     values_from = intel) %>%
  ## Calculating improvement scores for each listener
  dplyr::mutate(improv = posttest - pretest) %>%
  dplyr::ungroup()

# Merging the speaker and cognitive data back into the dataset. This is the main dataset we will use for analyses

## First getting relevant information from the primary dataset.
## For this analysis, we are using the age-corrected cognitive scores (variables that end in _c)
analysis_data <- pl_data %>%
  dplyr::select(c(id, speaker, list_sort_c:win_l)) %>%
  dplyr::distinct() %>%
  dplyr::right_join(intel_data, ., by = "id")

# Removing unneeded items from the environment

rm(intel_data)

```

### Descriptive Intelligibility Data Across Listeners

Across listeners, the mean and standard deviation values for pretest intelligibility, posttest intelligibility, and intelligibility difference is below.

```{r, warning = F, message = F}

intel_overall <- analysis_data %>%
    dplyr::select(id:speaker) %>%
    tidyr::pivot_longer(cols = posttest:improv,
                        names_to = "phase", 
                        values_to = "intel") %>%
    dplyr::mutate(phase = as.factor(phase),
                  phase = fct_relevel(phase, "pretest", "posttest", "improv"),
                  phase = recode(phase, pretest = "Pretest", posttest = "Posttest",
                                 improv = "Difference")) %>%
    dplyr::group_by(phase) %>%
    dplyr::summarize(Mean = mean(intel), SD = sd(intel)) %>%
    dplyr::ungroup() %>%
    gt::gt() %>%
    cols_label(phase = " ")

intel_overall

# Saving Table

intel_overall %>%
  gt::gtsave("Overall_Intel.html", path = "Tables")

```

### Intelligibility Improvement by Training Group

Listeners in this study were either assigned to perceptual training conditions for a male speaker with cerebellar ataxia (AM1) or a male speaker with Parkinson's disease (PDM10). We also calculated the mean and standard deviation in pretest intelligibility, posttest intelligibility, and intelligibility difference for each training group.

```{r, warning = F, message = F}

by_speaker <- analysis_data %>%
    dplyr::select(id:speaker) %>%
    tidyr::pivot_longer(cols = posttest:improv,
                        names_to = "phase", 
                        values_to = "intel") %>%
    dplyr::mutate(phase = as.factor(phase),
                  phase = fct_relevel(phase, "pretest", "posttest", "improv"),
                  phase = recode(phase, pretest = "Pretest", posttest = "Posttest",
                                 improv = "Difference")) %>%
    dplyr::group_by(speaker, phase) %>%
    dplyr::summarize(Mean = mean(intel), SD = sd(intel)) %>%
    dplyr::ungroup() %>%
    tidyr::pivot_wider(names_from = speaker,
                       values_from = c(Mean:SD)) %>%
    dplyr::relocate(SD_AM1, .before = Mean_PDM10) %>%
    gt::gt() %>%
    fmt_number(columns = "Mean_AM1":"SD_PDM10", decimals = 2) %>%
    tab_spanner(label = "AM1",
                columns = c(Mean_AM1, SD_AM1)) %>%
    tab_spanner(label = "PDM10",
                columns = c(Mean_PDM10, SD_PDM10)) %>%
    cols_label(phase = " ",
               Mean_AM1 = "Mean",
               SD_AM1 = "SD",
               Mean_PDM10 = "Mean",
               SD_PDM10 = "SD")

by_speaker

# Saving the Table

by_speaker %>%
  gt::gtsave("Intel_by_speaker.html", path = "Tables")

# Removing unneeded items

rm(by_speaker, intel_overall)

```

### Pretest vs Posttest Plot

A visual showing difference in pretest and posttest intelligibility scores for all listeners. The mean change in intelligibility for each speaker group is noted by the darker bolder lines. Note the variability in the individual listener responses.

```{r, warning = F, message = F}

# Creating a Custom Color Palette
my_pal <- c("#160F29", "#246A73", "#368F8B", "#F3DFC1", "#DDBEA8")

analysis_data %>%
  dplyr::select(c(id:pretest, speaker)) %>%
  tidyr::pivot_longer(cols = posttest:pretest,
                      names_to = "phase",
                      values_to = "intel") %>%
  dplyr::mutate(phase = as.factor(phase),
                phase = fct_relevel(phase, "pretest", "posttest")) %>%
  ggplot() +
  aes(x = phase,
      y = intel,
      group = id,
      color = speaker) +
  geom_line(alpha = 0.3) +
  stat_summary(aes(group = speaker),
               fun.y = mean, geom = "line", linewidth = 2) +
  facet_wrap("speaker") +
  scale_color_manual(values = my_pal) +
  labs(x = "Phase", y = "Intelligibility") +
  theme_bw() +
  theme(legend.position = "none")

# Save the plot

ggsave("Plots/Pre_Post.png", plot = last_plot())

```

### 2023-08-17 Preliminary Analyses/Preliminary Data Analysis.Rmd
Full prelim analyses completed. For 2024 MSC proposal

@@
 library(gt)
+library(reshape2) #install.packages("reshape2")
+library(ggcorrplot) #install.packages("ggcorrplot")
+library(patchwork) #install.packages("patchwork")
 
@@
 
-analysis_data %>%
+pre_post <- analysis_data %>%
   dplyr::select(c(id:pretest, speaker)) %>%
@@
   theme_bw() +
-  theme(legend.position = "none")
+  theme(legend.position = "none", aspect.ratio = 1)
+
+pre_post
 
@@
 ```
+
+## Cognitive Subtests
+
+In this section, we will now look at the listeners' scores on the subtests from the NIH Toolbox Cognitive Battery.
+The assessments that were administered to the participants are listed below.
+In this analysis, we are using the age-corrected standard scores.
+
+-   List Sort Working Memory Test (list_sort_c)
+
+-   Flanker Inhibitory Control and Attention Test (flanker_c)
+
+-   Dimensional Change Card Sort Test (card_sort_c)
+
+    -   We also refer to this as cognitive flexibility
+
+-   Picture Vocabulary Test (vocab_c)
+
+-   Pattern Comparison Processing Speed Test (pattern_c)
+
+-   Picture Sequence Memory Test (pic_seq_c)
+
+The dataset also contains the words-in--noise thresholds for the participants' right (win_r) and left (win_l).
+We determined the participant's best threshold (e.g.
+the ear with the lower threshold score) and created a new variable called best_win.
+To see the full data processing steps, click "show code".
+
+```{r}
+
+# Determining ear with the lowest words-in-noise threshold (best_win)
+
+analysis_data <- analysis_data %>%
+  dplyr::mutate(best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
+  dplyr::select(!c(win_r, win_l, fluid_cog_c))
+
+```
+
+### Overall Cognitive Scores
+
+The descriptive statistics for performance on each of the cognitive subtests are
+
+```{r, warning = F, message = F}
+
+cog_des <- analysis_data %>%
+  dplyr::select(!c(posttest:speaker)) %>%
+  tidyr::pivot_longer(cols = list_sort_c:best_win,
+                      names_to = "cog",
+                      values_to = "score") %>%
+  dplyr::group_by(cog) %>%
+  dplyr::summarize(Mean = mean(score, na.rm = T), SD = sd(score, na.rm = T)) %>%
+  gt::gt() %>%
+  fmt_number(columns = "Mean":"SD", decimals = 2) %>%
+  cols_label(cog = " ")
+
+cog_des
+
+cog_des %>%
+  gt::gtsave("Overall_cog.html", path = "Tables")
+
+```
+
+### Cognitive Subtest Scores per Training Group
+
+We are now comparing the mean and standard deviation in these cognitive scores for listeners who were trained with AM1 vs PDM10.
+
+```{r, warning = F, message = F}
+
+cog_by_speaker <- analysis_data %>%
+  dplyr::select(!c(posttest:improv)) %>%
+  tidyr::pivot_longer(cols = list_sort_c:best_win,
+                      names_to = "cog",
+                      values_to = "score") %>%
+  dplyr::group_by(cog, speaker) %>%
+  dplyr::summarize(Mean = mean(score, na.rm = T), SD = sd(score, na.rm = T)) %>%
+  dplyr::ungroup() %>%
+  tidyr::pivot_wider(names_from = speaker,
+                     values_from = c(Mean:SD)) %>%
+  dplyr::relocate(SD_AM1, .before = Mean_PDM10) %>%
+  gt::gt() %>%
+  fmt_number(columns = "Mean_AM1":"SD_PDM10", decimals = 2) %>%
+  tab_spanner(label = "AM1",
+              columns = c(Mean_AM1, SD_AM1)) %>%
+  tab_spanner(label = "PDM10",
+              columns = c(Mean_PDM10, SD_PDM10)) %>%
+  cols_label(cog = " ",
+             Mean_AM1 = "Mean",
+             SD_AM1 = "SD",
+             Mean_PDM10 = "Mean",
+             SD_PDM10 = "SD")
+
+cog_by_speaker
+
+cog_by_speaker %>%
+  gt::gtsave("cog_by_speaker.html", path = "Tables")
+
+```
+
+# Correlations
+
+In this study, we are particularly interested in the relationships between these cognitive subtests and initial intelligibility (pretest) and intelligibility difference between pretest and posttest (improv).
+In this preliminary analysis, we first started by calculating the correlations between these measures for 1) listeners trained with AM1, and 2) listeners trained with PDM10.
+
+## Correlation Matrix for Listeners assigned to AM1
+
+```{r, warning = F, message = F}
+
+AM1_corr <- analysis_data %>%
+  dplyr::filter(speaker == "AM1") %>%
+  dplyr::select(c(pretest:improv, list_sort_c:best_win)) %>%
+  dplyr::rename("Initial Intelligibility" = pretest,
+                "Intelligibility Improvement" = improv,
+                "Working Memory" = list_sort_c,
+                "Inhibitory Control" = flanker_c,
+                "Cognitive Flexibility" = card_sort_c,
+                "Receptive Vocabulary" = vocab_c,
+                "Processing Speed" = pattern_c,
+                "Speech in Noise Threshold" = best_win,
+                "Picture Sequence Memory" = pic_seq_c)
+
+AM1_corr <- round(cor(AM1_corr, use = "pairwise.complete.obs"), 2)
+
+get_lower_tri<-function(AM1_corr){
+    AM1_corr[upper.tri(AM1_corr)]<- NA
+    return(AM1_corr)
+  }
+
+AM1_lower_cor <- get_lower_tri(AM1_corr)
+
+AM1_lower_cor <- melt(AM1_lower_cor, na.rm = T)
+
+AM1 <- AM1_lower_cor %>%
+  ggplot() +
+  aes(x = Var1,
+      y = Var2,
+      fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = my_pal[1], high = my_pal[1], mid = "white",
+                      midpoint = 0, limit = c(-1,1), space = "Lab",
+                      name = "Pearson\nCorrelation") +
+  geom_text(aes(Var1, Var2, label = value), color = "black", size = 3) +
+  labs(x = " ",
+       y = " ") +
+  ggtitle('AM1') +
+  theme_bw() +
+  theme(axis.text.x = element_text(color = "black", angle = 45, hjust = 1),
+        aspect.ratio = 1)
+
+AM1
+
+ggsave("Plots/AM1_corr.png", plot = last_plot())
+
+```
+
+## Correlation Martix for Listeners Assigned to PDM10
+
+```{r, warning = F, message = F}
+
+PDM10_corr <- analysis_data %>%
+  dplyr::filter(speaker == "PDM10") %>%
+  dplyr::select(c(pretest:improv, list_sort_c:best_win)) %>%
+  dplyr::rename("Initial Intelligibility" = pretest,
+                "Intelligibility Improvement" = improv,
+                "Working Memory" = list_sort_c,
+                "Inhibitory Control" = flanker_c,
+                "Cognitive Flexibility" = card_sort_c,
+                "Receptive Vocabulary" = vocab_c,
+                "Processing Speed" = pattern_c,
+                "Speech in Noise Threshold" = best_win,
+                "Picture Sequence Memory" = pic_seq_c)
+
+PDM10_corr <- round(cor(PDM10_corr, use = "pairwise.complete.obs"), 2)
+
+get_lower_tri<-function(PDM10_corr){
+    PDM10_corr[upper.tri(PDM10_corr)]<- NA
+    return(PDM10_corr)
+  }
+
+PDM10_lower_cor <- get_lower_tri(PDM10_corr)
+
+PDM10_lower_cor <- melt(PDM10_lower_cor, na.rm = T)
+
+PDM10 <- PDM10_lower_cor %>%
+  ggplot() +
+  aes(x = Var1,
+      y = Var2,
+      fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = my_pal[2], high = my_pal[2], mid = "white",
+                      midpoint = 0, limit = c(-1,1), space = "Lab",
+                      name = "Pearson\nCorrelation") +
+  geom_text(aes(Var1, Var2, label = value), color = "black", size = 3) +
+  labs(x = " ",
+       y = " ") +
+  ggtitle('PDM10') +
+  theme_bw() +
+  theme(axis.text.x = element_text(color = "black", angle = 45, hjust = 1),
+        aspect.ratio = 1)
+
+PDM10
+
+ggsave("Plots/PDM10_corr.png", plot = last_plot())
+
+```
+
+```{r, echo = F, eval = F}
+
+figure_1 <- (AM1 | PDM10) /
+  pre_post
+
+figure_1
+
+ggsave("Plots/Full_figure.png", plot = last_plot(), width = 15, height = 15, units = "in")
+
+```

### 2023-12-18 Manuscript Analyses/manuscript_analysis.Rmd
Created analysis rmd document

---
title: Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older
  Adult Listeners
author: "Lansford, Hirsch, Barrett, & Borrie"
date: "`r Sys.Date()`"
output: 
  github_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This document contains the analysis code and output for the manuscript entitled "Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older Adult Listeners". These results will also be presented at the Biannual Motor Speech Conference held in San Diego, CA from February 21-24, 2024.

All data processing and analyses was conducted using R Version 4.3.2

```{r, echo = F, warning = F, message = F}

# Loading in needed packages
library(tidyverse) #install.packages("tidyverse")
library(rio) #install.packages("rio")
library(gt) #install.packages("gt")
library(reshape2) #install.packages("reshape2")
library(ggcorrplot) #install.packages("ggcorrplot")
library(patchwork) #install.packages("patchwork")
library(janitor) #install.packages("janitor")
library(fs) #install.packages("fs")
library(furniture) #install.packages("furniture")
library(caret) #install.packages("caret")
library(effectsize) #install.packages("effectsize")
library(parameters) #install.packages("parameters")
library(performance) #install.packages("performance")
library(bayestestR) #install.packages("bayestestR)
library(rstanarm) #install.packages("rstanarm")

```

```{r, echo = F, warning = F, message = F}

# Functions used in this code

## Function for determining variable importance
var_imp <- function(mod, label) {
  varImp(mod)$importance %>%
    rownames_to_column(var = "Variable") %>%
    mutate(Overall = Overall/max(Overall)) %>%
    rename(!!label := Overall, 
          var = Variable)
}

## Function for model training
training <- function(data, method, int) {
  form = if (isTRUE(int)) {
    d2 = model.matrix(pwc ~ . * ., data = data)[, -1] %>%
      as_tibble() %>%
      janitor::clean_names()
    d2$pwc = data$pwc
  } else {
    d2 = data
    train(
      pwc ~.,
      data = d2,
      preProcess = c("center", "scale"),
      method = "repeatedcv",
      number = 5,
      repeats = 10
    )
  }
}

```

# Descriptives

## Intelligibility

```{r}

```

## Cognition

## Hearing Threshold

### 2023-12-20 Manuscript Analyses/manuscript_analysis.Rmd
Reformatted analysis rmd file
participant demo and cog des stats

@@
 
-## Intelligibility
+## Participant Demographics
 
 ```{r}
+
+demo <- rio::import("participant_demo.csv")
 
@@
 
+```{r}
+
+cog <- rio::import("cleaned_data.csv") %>%
+  dplyr::select(c(id, speaker, list_sort_c:win_l)) %>%
+  dplyr::mutate(best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
+  dplyr::distinct()
+
+age <- demo %>%
+  select(id, age)
+
+cog_scores <- left_join(age, cog, by = "id")
+
+cog_scores %>%
+  dplyr::group_by(speaker) %>%
+  furniture::table1(age, list_sort_c, flanker_c, card_sort_c, vocab_c, pattern_c, 
+                    pic_seq_c, fluid_cog_c, best_win,
+                    test = T, 
+                    export = "cog_score")
+
+```
+
+## Intelligibility
+
 ## Hearing Threshold

### 2023-12-20 Manuscript Analyses/manuscript_analysis.Rmd
participant summary updated

@@
                     pic_seq_c, fluid_cog_c, best_win,
-                    test = T, 
+                    test = T, type = c("simple", "condensed"), 
                     export = "cog_score")

### 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
fixed cog means table

--- 2023-12-18 Manuscript Analyses/manuscript_analysis.Rmd
@@
 library(gt) #install.packages("gt")
+library(gtsummary) #install.packages("gtsummary")
 library(reshape2) #install.packages("reshape2")
@@
 library(rstanarm) #install.packages("rstanarm")
+
+# Load in dataset
+
+demo <- rio::import("participant_demo.csv")
+
+data <- rio::import("cleaned_data.csv")
 
@@
 
+```{r}
+
+# Calculating pretest and posttest intelligibility for the listeners
+pl_int <- data %>%
+  dplyr::group_by(id, speaker, type) %>%
+  dplyr::mutate(pwc = (sum(correct_words)/sum(target_number))*100,
+                best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
+  dplyr::summarize(mean_pwc = mean(pwc, na.rm = T),
+                   across(c(contains("_c"), contains("_u"), contains("win")),
+                          ~first(.x)
+                          )) %>%
+  dplyr::ungroup()
+
+# Subsetting age from demo df
+
+age <- demo %>%
+  select(id, age)
+
+# Merging listener age into pl_int
+
+pl_int <- dplyr::left_join(age, pl_int, by = "id")
+
+```
+
 # Descriptives
 
-## Intelligibility
+## Participant Demographics
+
+TBD
 
@@
 
-## Hearing Threshold
+```{r}
+
+int_table <- pl_int %>%
+  dplyr::filter(type == "pretest") %>%
+  dplyr::select(id, speaker, age, ends_with("_c"), best_win) %>%
+  dplyr::select(-fluid_cog_c) %>%
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Picture Sequence Memory` = pic_seq_c,
+    `Words in Noise Threshold` = best_win
+  ) %>%
+  group_by(id, speaker) %>% 
+  summarize(across(everything(), first)) %>% 
+  ungroup() %>% 
+  select(-id) %>% 
+  tbl_summary(
+    by = "speaker",
+    statistic = list(all_continuous() ~ "{mean} ({sd})"),
+    missing = "no",
+    digits = list(everything() ~ c(2))
+  ) %>% 
+  add_p() %>%
+  as_gt()
+
+int_table
+
+int_table %>%
+  gt::gtsave("Tables/means_tabel.html")
+
+```
+
+## Intelligibility
+
+```{r}
+
+# Intelligibiltiy Descriptives Table
+
+```

### 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
Intelligibility summary stats

@@
 
-# Intelligibiltiy Descriptives Table
+# Intelligibility Descriptives Table
+
+speaker_intel <- pl_int %>%
+  dplyr::mutate(type = as.factor(type),
+                type = fct_relevel(type, "pretest", "posttest")) %>%
+  dplyr::group_by(speaker, type) %>%
+  dplyr::summarize(pwc = mean(mean_pwc),
+                   sd = sd(mean_pwc)) %>%
+  dplyr::ungroup() %>%
+  tidyr::pivot_wider(names_from = speaker,
+                     values_from = c(pwc:sd)) %>%
+  dplyr::relocate(sd_AM1, .after = pwc_AM1) %>%
+  gt::gt() %>%
+    fmt_number(columns = "pwc_AM1":"sd_PDM10", decimals = 2) %>%
+    tab_spanner(label = "AM1",
+                columns = c(pwc_AM1, sd_AM1)) %>%
+    tab_spanner(label = "PDM10",
+                columns = c(pwc_PDM10, sd_PDM10)) %>%
+    cols_label(type = " ",
+               pwc_AM1 = "Mean",
+               sd_AM1 = "SD",
+               pwc_PDM10 = "Mean",
+               sd_PDM10 = "SD")
+
+speaker_intel
+
+speaker_intel %>%
+  gt::gtsave("Tables/intel_des.html")
 

### 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
Pre-post & correlation figures

@@
 
+pl_int <- pl_int %>%
+  dplyr::mutate(type = as.factor(type),
+                type = fct_relevel(type, "pretest", "posttest"))
+
 ```
@@
 ```
+
+### Pretest - Posttest Plot
+
+```{r}
+
+pl_int %>%
+  ggplot() +
+  aes(x = type,
+      y = mean_pwc,
+      group = id) +
+  geom_line(alpha = 0.3) +
+  stat_summary(aes(group = speaker),
+               fun.y = mean, geom = "line", linewidth = 2) +
+  facet_wrap("speaker") +
+  labs(x = "Phase", y = "Intelligibility") +
+  theme_bw() +
+  theme(legend.position = "none", aspect.ratio = 1)
+
+```
+
+# Results
+
+## Correlations
+
+### AM1
+
+```{r}
+
+cor_df <- pl_int %>%
+  tidyr::pivot_wider(names_from = type,
+                     values_from = mean_pwc) %>%
+  dplyr::mutate(improvement = posttest - pretest) %>%
+  dplyr::select(id, speaker, ends_with("_c"), best_win, pretest, improvement)
+
+AM1_cor <- cor_df %>%
+  dplyr::filter(speaker == "AM1") %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c)) %>%
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Picture Sequence Memory` = pic_seq_c,
+    `Words in Noise Threshold` = best_win
+  ) %>%
+  dplyr::rename_all(snakecase::to_title_case) %>%
+  cor(use = "pairwise.complete.obs") %>%
+  ggcorrplot(
+    type = "lower",
+    outline.col = "white",
+    colors = c("#6D9EC1", "white", "#E46726"),
+    lab = TRUE,
+    insig = "blank",
+    title = "Ataxic", 
+    legend.title = "Correlation"
+  )
+
+AM1_cor
+
+```
+
+### PDM10
+
+```{r}
+
+PDM10_cor <- cor_df %>%
+  dplyr::filter(speaker == "PDM10") %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c)) %>%
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Picture Sequence Memory` = pic_seq_c,
+    `Words in Noise Threshold` = best_win
+  ) %>%
+  dplyr::rename_all(snakecase::to_title_case) %>%
+  cor(use = "pairwise.complete.obs") %>%
+  ggcorrplot(
+    type = "lower",
+    outline.col = "white",
+    colors = c("#6D9EC1", "white", "#E46726"),
+    lab = TRUE,
+    insig = "blank",
+    title = "Parkinson's Disease", 
+    legend.title = "Correlation"
+  )
+
+PDM10_cor
+
+```
+
+```{r}
+
+library(patchwork)
+AM1_cor + PDM10_cor + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+ggsave("Plots/cor_fig.png", width = 20, height = 6, dpi = 300, units = "in")
+
+```

### 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
writing model functions - wip

--- 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
@@
 library(rstanarm) #install.packages("rstanarm")
+library(afex) #install.packages("afex")
 
@@
 # Functions used in this code
+
+## Plot importance function
+plot_importance = function(mods, labels){
+  map2(mods, labels, ~var_imp(.x, .y)) %>% 
+    reduce(full_join, by = "var") %>% 
+    ungroup() %>% 
+    pivot_longer(-var) %>% 
+    group_by(var) %>% 
+    mutate(avg_imp = mean(value, na.rm=TRUE)) %>% 
+    ungroup() %>% 
+    arrange(avg_imp) %>% 
+    mutate(var = fct_inorder(var))
+}
 
@@
 pl_int <- dplyr::left_join(age, pl_int, by = "id")
+
+pl_int <- pl_int %>%
+  dplyr::mutate(type = as.factor(type),
+                type = fct_relevel(type, "pretest", "posttest"))
 
@@
 ```
+
+### Pretest - Posttest Plot
+
+```{r}
+
+pl_int %>%
+  ggplot() +
+  aes(x = type,
+      y = mean_pwc,
+      group = id) +
+  geom_line(alpha = 0.3) +
+  stat_summary(aes(group = speaker),
+               fun.y = mean, geom = "line", linewidth = 2) +
+  facet_wrap("speaker") +
+  labs(x = "Phase", y = "Intelligibility") +
+  theme_bw() +
+  theme(legend.position = "none", aspect.ratio = 1)
+
+```
+
+# Results
+
+## Correlations
+
+### AM1
+
+```{r}
+
+cor_df <- pl_int %>%
+  tidyr::pivot_wider(names_from = type,
+                     values_from = mean_pwc) %>%
+  dplyr::mutate(improvement = posttest - pretest) %>%
+  dplyr::select(id, speaker, ends_with("_c"), best_win, pretest, posttest, improvement)
+
+AM1_cor <- cor_df %>%
+  dplyr::filter(speaker == "AM1") %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Picture Sequence Memory` = pic_seq_c,
+    `Words in Noise Threshold` = best_win
+  ) %>%
+  dplyr::rename_all(snakecase::to_title_case) %>%
+  cor(use = "pairwise.complete.obs") %>%
+  ggcorrplot(
+    type = "lower",
+    outline.col = "white",
+    colors = c("#6D9EC1", "white", "#E46726"),
+    lab = TRUE,
+    insig = "blank",
+    title = "Ataxic", 
+    legend.title = "Correlation"
+  )
+
+AM1_cor
+
+```
+
+### PDM10
+
+```{r}
+
+PDM10_cor <- cor_df %>%
+  dplyr::filter(speaker == "PDM10") %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Picture Sequence Memory` = pic_seq_c,
+    `Words in Noise Threshold` = best_win
+  ) %>%
+  dplyr::rename_all(snakecase::to_title_case) %>%
+  cor(use = "pairwise.complete.obs") %>%
+  ggcorrplot(
+    type = "lower",
+    outline.col = "white",
+    colors = c("#6D9EC1", "white", "#E46726"),
+    lab = TRUE,
+    insig = "blank",
+    title = "Parkinson's Disease", 
+    legend.title = "Correlation"
+  )
+
+PDM10_cor
+
+```
+
+```{r}
+
+library(patchwork)
+AM1_cor + PDM10_cor + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+ggsave("Plots/cor_fig.png", width = 20, height = 6, dpi = 300, units = "in")
+
+```
+
+## Pre-Post Change
+
+```{r}
+
+cor_df %>% 
+  dplyr::select(id, speaker, pretest, posttest) %>% 
+  tidyr::pivot_longer(pretest:posttest) %>% 
+  dplyr::group_by(speaker) %>% 
+  dplyr::group_nest() %>% 
+  dplyr::mutate(
+    mod = map(data, ~afex::aov_4(value ~ 1 + (name|id), data = .x))
+  ) %>% 
+  pull(mod)
+
+cor_df %>% 
+  dplyr::select(id, speaker, pretest, posttest) %>% 
+  tidyr::pivot_longer(pretest:posttest) %>% 
+  dplyr::group_by(speaker) %>% 
+  dplyr::group_nest() %>% 
+  dplyr::mutate(
+    mod = map(data, ~effectsize::cohens_d(value ~ name, data = .x))
+  ) %>% 
+  pull(mod)
+
+```
+
+## Models of Initial Intelligibility
+
+### Cognition
+
+TBD
+
+```{r}
+
+```

### 2023-12-23 Manuscript Analyses/manuscript_analysis.Rmd
Small formatting changes
Cleaned and formatted rmd code

@@
 
-All data processing and analyses was conducted using R Version 4.3.2
+The data preprocessing script can be found in the Manuscript Analyses subdirectory in this repo.
+
+All data processing and analyses was conducted using R Version 4.3.2.
 
@@
 
-```{r, echo = F, warning = F, message = F}
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+```{r, warning = F, message = F}
 
@@
 
+cor_df <- pl_int %>%
+  tidyr::pivot_wider(names_from = type,
+                     values_from = mean_pwc) %>%
+  dplyr::mutate(improvement = posttest - pretest) %>%
+  dplyr::select(id, speaker, ends_with("_c"), best_win, pretest, posttest, improvement)
+
+```
+
+```{r, echo = F, message = F, warning = F}
+
+# removing unneeded objects from the environment
+rm(age)
+
 ```
@@
 
-```{r}
+In this study, listeners were assigned to one of two speakers for perceptual training: a speaker with Ataxic dysarthria (AM1) or a speaker with Parkinson's disease (PDM10).
+Means and standard deviation for listener age, cognition, and word in noise hearing threshold for each condition are presented below.
+Wilcoxon rank sum tests were performed for each of the measures.
+None of the cognition or hearing measures were significantly different between the two groups.
+
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+Pretest and posttest intelligibility, as measured by percent words correct, for each of the two speaker conditions are presented below.
+On average, pretest intelligibility for AM1 was lower than PDM10.
+However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10.
+A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p < .001, d = 1.01).
+
+```{r, warning = F, message = F}
 
@@
 
+ggsave("Plots/Pre_post.png", plot = last_plot())
+
+```
+
+```{r}
+
+cor_df %>% 
+  dplyr::select(id, speaker, pretest, posttest) %>% 
+  tidyr::pivot_longer(pretest:posttest) %>% 
+  dplyr::group_by(speaker) %>% 
+  dplyr::group_nest() %>% 
+  dplyr::mutate(
+    mod = map(data, ~afex::aov_4(value ~ 1 + (name|id), data = .x))
+  ) %>% 
+  pull(mod)
+
+cor_df %>% 
+  dplyr::select(id, speaker, pretest, posttest) %>% 
+  tidyr::pivot_longer(pretest:posttest) %>% 
+  dplyr::group_by(speaker) %>% 
+  dplyr::group_nest() %>% 
+  dplyr::mutate(
+    mod = map(data, ~effectsize::cohens_d(value ~ name, data = .x))
+  ) %>% 
+  pull(mod)
+
 ```
@@
 
+The correlation matricies between all the cognitive measures, hearing threshold, initial intelligibility, and intelligibility improvement were conducted for each speaker condition.
+
 ### AM1
 
-```{r}
-
-cor_df <- pl_int %>%
-  tidyr::pivot_wider(names_from = type,
-                     values_from = mean_pwc) %>%
-  dplyr::mutate(improvement = posttest - pretest) %>%
-  dplyr::select(id, speaker, ends_with("_c"), best_win, pretest, posttest, improvement)
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+```{r, echo = F, warning = F, message = F}
 

### 2023-12-23 Manuscript Analyses/manuscript_analysis.Rmd
scripting elastic net models - wip

@@
 library(afex) #install.packages("afex")
+library(glmnet) #install.packages("glmnet")
 
-# Load in dataset
+# Load in datasets
 
+## Listener Demographic Information
 demo <- rio::import("participant_demo.csv")
 
+## Listener Intelligibility and Cognition Scores
 data <- rio::import("cleaned_data.csv")
-
-```
-
-```{r, warning = F, message = F}
-
-# Functions used in this code
-
-## Plot importance function
-plot_importance = function(mods, labels){
-  map2(mods, labels, ~var_imp(.x, .y)) %>% 
-    reduce(full_join, by = "var") %>% 
-    ungroup() %>% 
-    pivot_longer(-var) %>% 
-    group_by(var) %>% 
-    mutate(avg_imp = mean(value, na.rm=TRUE)) %>% 
-    ungroup() %>% 
-    arrange(avg_imp) %>% 
-    mutate(var = fct_inorder(var))
-}
-
-## Function for determining variable importance
-var_imp <- function(mod, label) {
-  varImp(mod)$importance %>%
-    rownames_to_column(var = "Variable") %>%
-    mutate(Overall = Overall/max(Overall)) %>%
-    rename(!!label := Overall, 
-          var = Variable)
-}
-
-## Function for model training
-training <- function(data, method, int) {
-  form = if (isTRUE(int)) {
-    d2 = model.matrix(pwc ~ . * ., data = data)[, -1] %>%
-      as_tibble() %>%
-      janitor::clean_names()
-    d2$pwc = data$pwc
-  } else {
-    d2 = data
-    train(
-      pwc ~.,
-      data = d2,
-      preProcess = c("center", "scale"),
-      method = "repeatedcv",
-      number = 5,
-      repeats = 10
-    )
-  }
-}
 
@@
 # removing unneeded objects from the environment
-rm(age)
+rm(age, data)
 
@@
 
-## Pre-Post Change
+## Models of Initial Intelligibility
+
+TBD
 
@@
 
-cor_df %>% 
-  dplyr::select(id, speaker, pretest, posttest) %>% 
-  tidyr::pivot_longer(pretest:posttest) %>% 
-  dplyr::group_by(speaker) %>% 
-  dplyr::group_nest() %>% 
-  dplyr::mutate(
-    mod = map(data, ~afex::aov_4(value ~ 1 + (name|id), data = .x))
-  ) %>% 
-  pull(mod)
+# Functions used in this code
 
-cor_df %>% 
-  dplyr::select(id, speaker, pretest, posttest) %>% 
-  tidyr::pivot_longer(pretest:posttest) %>% 
-  dplyr::group_by(speaker) %>% 
-  dplyr::group_nest() %>% 
-  dplyr::mutate(
-    mod = map(data, ~effectsize::cohens_d(value ~ name, data = .x))
-  ) %>% 
-  pull(mod)
+## Plot importance function
+plot_importance = function(mods, labels){
+  map2(mods, labels, ~var_imp(.x, .y)) %>% 
+    reduce(full_join, by = "var") %>% 
+    ungroup() %>% 
+    pivot_longer(-var) %>% 
+    group_by(var) %>% 
+    mutate(avg_imp = mean(value, na.rm=TRUE)) %>% 
+    ungroup() %>% 
+    arrange(avg_imp) %>% 
+    mutate(var = fct_inorder(var))
+}
+
+## Function for determining variable importance
+var_imp <- function(mod, label) {
+  varImp(mod)$importance %>%
+    rownames_to_column(var = "Variable") %>%
+    mutate(Overall = Overall/max(Overall)) %>%
+    rename(!!label := Overall, 
+          var = Variable)
+}
+
+## Function for model training
+training <- function(data, method, int) {
+  form = if (isTRUE(int)) {
+    d2 = model.matrix(mean_pwc ~ . * ., data = data)[, -1] %>%
+      as_tibble() %>%
+      janitor::clean_names()
+    d2$mean_pwc = data$mean_pwc
+  } else {
+    d2 = data
+    train(
+      mean_pwc ~ ., 
+      data = d2, 
+      preProcess = c("center", "scale"),
+      method = method, 
+      trControl = caret::trainControl(
+        method = "repeatedcv",
+        number = 5,
+        repeats = 10
+    ))
+  }
+}
 
@@
 
-## Models of Initial Intelligibility
-
-### Cognition
-
-TBD
-
 ```{r}
 
+set.seed(7036)
+
+mod_fun = function(speaker, type){
+  subsetted = pl_int %>% 
+    filter(type == {{type}}) %>% 
+    filter(speaker == {{speaker}}) %>% 
+    select(mean_pwc, ends_with("_c"), best_win) %>% 
+    drop_na(mean_pwc, ends_with("_c"), best_win) %>% 
+    select(-contains("fluid"))
+
+  mod.1 = training(subsetted, "glmnet", int = FALSE)
+  mod.2 = training(subsetted, "glmnet", int = TRUE)
+
+  return(list(mod.1, mod.2))
+}
+
+plot_fun = function(mods, title){
+  plot_importance(
+    mods = mods,
+    labels = c("main", "int")
+  ) %>% 
+    drop_na(value) %>% 
+    mutate(name = factor(
+      name, 
+      levels = c("main", "int"),
+      labels = c(
+        paste0("Main Effects"),
+        paste0("Interactions")
+    ))) %>% 
+    filter(name == "Interactions") %>% 
+    mutate(var = str_replace(var, "flanker_c", "Inhibitory Control of Attention"),
+           var = str_replace(var, "card_sort_c", "Cognitive Flexibility"),
+           var = str_replace(var, "vocab_c", "Vocabulary Knowledge"),
+           var = str_replace(var, "pattern_c", "Processing Speed"),
+           var = str_replace(var, "list_sort_c", "Working Memory"),
+           var = str_replace(var, "pic_seq_c", "Picture Sequence Memory"),
+           var = str_replace(var, "best_win", "Words in Noise Threshold"),
+           var = str_replace(var, "_", " x ")) %>% 
+    arrange(value) %>% 
+    mutate(var = fct_inorder(var)) %>% 
+    ggplot(aes(x = value, y = var, color = value)) +
+    geom_segment(aes(xend = 0, yend = var)) +
+    geom_point(size = 2) +
+    facet_wrap(~name, scales = "free") +
+    labs(x = "Relative Importance",
+         y = "",
+         title = {{title}}) +
+    scale_color_viridis_c(option = "magma", end = .8) +
+    theme(plot.title.position = "plot")
+}
+
+mods1 = mod_fun("AM1", "pretest")
+mods2 = mod_fun("PDM10", "pretest")
+
+p1 = plot_fun(mods1, "a) Ataxic")
+p2 = plot_fun(mods2, "b) PD")
+
 ```

### 2023-12-28 Manuscript Analyses/manuscript_analysis.Rmd
Small edits to des stats code

@@
                 best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
-  dplyr::summarize(mean_pwc = mean(pwc, na.rm = T),
+  dplyr::summarize(pwc = mean(pwc, na.rm = T),
                    across(c(contains("_c"), contains("_u"), contains("win")),
@@
                           )) %>%
-  dplyr::ungroup()
+  dplyr::ungroup() %>%
+  dplyr::mutate(type = as.factor(type),
+                type = fct_relevel(type, "pretest", "posttest"))
 
@@
 
-pl_int <- pl_int %>%
-  dplyr::mutate(type = as.factor(type),
-                type = fct_relevel(type, "pretest", "posttest"))
-
 cor_df <- pl_int %>%
   tidyr::pivot_wider(names_from = type,
-                     values_from = mean_pwc) %>%
+                     values_from = pwc) %>%
   dplyr::mutate(improvement = posttest - pretest) %>%
@@
 
-int_table <- pl_int %>%
+cog_table <- pl_int %>%
   dplyr::filter(type == "pretest") %>%
@@
 
-int_table
+cog_table
 
-int_table %>%
+cog_table %>%
   gt::gtsave("Tables/means_tabel.html")
@@
   dplyr::group_by(speaker, type) %>%
-  dplyr::summarize(pwc = mean(mean_pwc),
-                   sd = sd(mean_pwc)) %>%
+  dplyr::summarize(m_pwc = mean(pwc),
+                   sd_pwc = sd(pwc)) %>%
   dplyr::ungroup() %>%
   tidyr::pivot_wider(names_from = speaker,
-                     values_from = c(pwc:sd)) %>%
-  dplyr::relocate(sd_AM1, .after = pwc_AM1) %>%
+                     values_from = c(m_pwc:sd_pwc)) %>%
+  dplyr::relocate(sd_pwc_AM1, .after = m_pwc_AM1) %>%
   gt::gt() %>%
-    fmt_number(columns = "pwc_AM1":"sd_PDM10", decimals = 2) %>%
+    fmt_number(columns = "m_pwc_AM1":"sd_pwc_PDM10", decimals = 2) %>%
     tab_spanner(label = "AM1",
-                columns = c(pwc_AM1, sd_AM1)) %>%
+                columns = c(m_pwc_AM1, sd_pwc_AM1)) %>%
     tab_spanner(label = "PDM10",
-                columns = c(pwc_PDM10, sd_PDM10)) %>%
+                columns = c(m_pwc_PDM10, sd_pwc_PDM10)) %>%
     cols_label(type = " ",
-               pwc_AM1 = "Mean",
-               sd_AM1 = "SD",
-               pwc_PDM10 = "Mean",
-               sd_PDM10 = "SD")
+               m_pwc_AM1 = "Mean",
+               sd_pwc_AM1 = "SD",
+               m_pwc_PDM10 = "Mean",
+               sd_pwc_PDM10 = "SD")
 
@@
   aes(x = type,
-      y = mean_pwc,
+      y = pwc,
       group = id) +
@@
 ggsave("Plots/cor_fig.png", width = 20, height = 6, dpi = 300, units = "in")
+
+rm(AM1_cor, PDM10_cor, cog_table, speaker_intel)
 

### 2023-12-28 Manuscript Analyses/manuscript_analysis.Rmd
updated model functions

@@
   form = if (isTRUE(int)) {
-    d2 = model.matrix(mean_pwc ~ . * ., data = data)[, -1] %>%
+    d2 = model.matrix(pwc ~ . * ., data = data)[, -1] %>%
       as_tibble() %>%
       janitor::clean_names()
-    d2$mean_pwc = data$mean_pwc
+    d2$pwc = data$pwc
   } else {
@@
     train(
-      mean_pwc ~ ., 
+      pwc ~ ., 
       data = d2, 
@@
     filter(speaker == {{speaker}}) %>% 
-    select(mean_pwc, ends_with("_c"), best_win) %>% 
-    drop_na(mean_pwc, ends_with("_c"), best_win) %>% 
+    select(pwc, ends_with("_c"), best_win) %>% 
+    drop_na(pwc, ends_with("_c"), best_win) %>% 
     select(-contains("fluid"))

### 2024-01-03 Manuscript Analyses/manuscript_analysis.Rmd
Initial Intelligibility Models

@@
     d2 = data
+  }
     train(
@@
         repeats = 10
-    ))
-  }
+    )
+  )
 }
@@
 ```
+
+```{r}
+
+p2
+
+```
+
+```{r}
+
+in_and_out <- function(mods, speaker) {
+  out_sample_r2 = map_dbl(mods, ~max(.x$results$Rsquared))
+  out_sample_rmse = map_dbl(mods, ~min(.x$results$RMSE)) 
+  tibble(
+    speaker = speaker,
+    mods = c("Main Effects", "Interactions"),
+    out_sample_r2,
+    out_sample_rmse
+  )
+}
+
+AM1_initial_mod <- in_and_out(mods1, "Ataxic")
+
+PDM10_initial_mod <- in_and_out(mods2, "PD")
+
+initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)
+
+initial_mods %>%
+  gt::gt() %>%
+  cols_label(speaker = "Speaker",
+             mods = "Model Specification",
+             out_sample_r2 = "R\U00B2",
+             out_sample_rmse = "RMSE")
+
+```
+
+```{r}
+
+t_for_diff <- function(mods){
+  samps = resamples(list(
+    main = mods[[1]],
+    int = mods[[2]]
+  ))
+  summary(samps)
+  diff(samps) %>%
+    summary()
+}
+
+t_for_diff(mods1)
+t_for_diff(mods2)
+
+```
+
+```{r}
+
+effect_data <- function(mod){
+  mod[[2]]$trainingData %>%
+    mutate(preds = predict(mod[[2]]))
+}
+
+effect_plot <- function(mod, var, var2 = NULL, int = TRUE, num = 5) {
+  dat = effect_data(mod)
+
+  if (isFALSE(int)){
+    dat %>%
+      ggplot() +
+      aes(x={{var}}, 
+          y = .outcome) +
+      geom_point() +
+      geom_smooth(method = "lm")
+  } else {
+    dat %>%
+      ggplot() +
+      aes(x = {{var}},
+          y= .outcome,
+          group = cut_interval({{var2}}, num),
+          color = cut_interval({{var2}}, num)) +
+      geom_point() +
+      geom_smooth(method = "lm") +
+      theme(legend.position = "bottom")
+  }
+}
+
+# AM1 Effect Plots
+
+effect_plot(mods1, pic_seq_c, best_win)
+effect_plot(mods1, best_win, pic_seq_c)
+effect_plot(mods1, best_win, int = F)
+effect_plot(mods1, list_sort_c, vocab_c)
+effect_plot(mods1, vocab_c, list_sort_c)
+effect_plot(mods1, list_sort_c, pattern_c)
+effect_plot(mods1, pattern_c, list_sort_c)
+
+# PDM10 Effect Plots
+
+effect_plot(mods2, vocab_c, pattern_c)
+effect_plot(mods2, pattern_c, vocab_c)
+effect_plot(mods2, best_win, int = F)
+effect_plot(mods2, flanker_c, best_win)
+effect_plot(mods2, best_win, flanker_c)
+effect_plot(mods2, list_sort_c, pattern_c)
+effect_plot(mods2, pattern_c, list_sort_c)
+effect_plot(mods2, vocab_c, pic_seq_c)
+effect_plot(mods2, pic_seq_c, vocab_c)
+effect_plot(mods2, card_sort_c, vocab_c)
+effect_plot(mods2, vocab_c, card_sort_c)
+
+```

### 2024-01-03 Manuscript Analyses/manuscript_analysis.Rmd
intelligibility change models

@@
 
-TBD
-
 ```{r, warning = F, message = F}
@@
 
-effect_plot <- function(mod, var, var2 = NULL, int = TRUE, num = 5) {
+effect_plot <- function(mod, var, var2 = NULL, int = TRUE, num = 3) {
   dat = effect_data(mod)
@@
 ```
+
+## Models of Cognition and Intelligibility Change
+
+```{r}
+
+mod_fun2 <- function(speaker, title) {
+  subsetted = cor_df %>%
+    dplyr::select(-c(fluid_cog_c, improvement)) %>%
+    dplyr::mutate(pwc_diff = resid(lm(posttest ~ pretest))) %>%
+    dplyr::select(pwc_diff, ends_with("_c"), speaker) %>%
+    tidyr::drop_na(pwc_diff, ends_with("_c"), speaker) %>%
+    dplyr::filter(speaker == {{speaker}}) %>%
+    dplyr::select(-speaker) %>%
+    rename(pwc = pwc_diff)
+
+  mod.1 = training(subsetted, "glmnet", int = F)
+  mod.2 = training(subsetted, "glmnet", int = T)
+
+  return(list(mod.1, mod.2))
+
+}
+
+mods12 = mod_fun2("AM1")
+mods22 = mod_fun2("PDM10")
+
+p12 = plot_fun(mods12, "a) Ataxic")
+p22 = plot_fun(mods22, "b) PD")
+
+p12
+```
+
+```{r}
+
+p22
+
+```
+
+```{r}
+
+AM1_change_mod <- in_and_out(mods12, "Ataxic")
+
+PDM10_change_mod <- in_and_out(mods22, "PD")
+
+change_mods <- rbind(AM1_change_mod, PDM10_change_mod)
+
+change_mods %>%
+  gt::gt() %>%
+  cols_label(speaker = "Speaker",
+             mods = "Model Specification",
+             out_sample_r2 = "R\U00B2",
+             out_sample_rmse = "RMSE")
+
+```
+
+```{r}
+
+t_for_diff(mods12)
+t_for_diff(mods22)
+
+```
+
+```{r}
+
+## AM1 Effect Plots
+
+effect_plot(mods12, list_sort_c, vocab_c)
+effect_plot(mods12, vocab_c, list_sort_c)
+effect_plot(mods12, list_sort_c, int = F)
+effect_plot(mods12, pattern_c, int = F)
+effect_plot(mods12, list_sort_c, flanker_c)
+effect_plot(mods12, flanker_c, list_sort_c)
+
+## PDM10 Effect Plots
+
+effect_plot(mods22, vocab_c, pic_seq_c)
+effect_plot(mods22, pic_seq_c, vocab_c)
+effect_plot(mods22, vocab_c, int = F)
+effect_plot(mods22, list_sort_c, flanker_c)
+effect_plot(mods22, flanker_c, list_sort_c)
+
+```

### 2024-01-03 Manuscript Analyses/manuscript_analysis.Rmd
overall participant demographics

@@
 
-TBD
+The overall demographic information for the participants are below.
 
 ```{r}
+
+demo_table <- demo %>%
+  dplyr::select(-id) %>%
+  tbl_summary(type = list(age ~ "continuous",
+                          gender ~ "categorical",
+                          race ~ "categorical",
+                          ethnicity ~ "categorical"),
+              statistic = list(all_continuous() ~ "{mean} ({sd})",
+                              all_categorical() ~ "{n} ({p}%)"),
+              digits = list(everything() ~ c(2))) %>%
+  as_gt()
+
+demo_table
+
+demo_table %>%
+  gt::gtsave("Tables/demo_table.html")
 

### 2024-01-04 Manuscript Analyses/manuscript_analysis.Rmd
reorganizing rmd file

@@
 
-All data processing and analyses was conducted using R Version 4.3.2.
+All data processing and analyses were conducted using R Version 4.3.2.
 
@@
 ```
+
+First, pretest and posttest intelligibility was calculated as percent words correct (pwc) for each listener.
 
@@
 
-The overall demographic information for the participants are below.
+A total of 60 older adult listeners participated in the study. The overall demographic information for the participants are below.
 
@@
 
+```{r, echo = F, warning = F, message = F}
+
+# Removing unneeded items from the environment
+
+rm(demo)
+
+```
+
 ## Cognition
@@
 Wilcoxon rank sum tests were performed for each of the measures.
-None of the cognition or hearing measures were significantly different between the two groups.
+None of the cognition or hearing measures were significantly different between the two groups of listeners.
 
@@
   labs(x = "Phase", y = "Intelligibility") +
-  theme_bw() +
+  theme_classic() +
   theme(legend.position = "none", aspect.ratio = 1)
@@
 
+# Customize plot colors
+
+library(LaCroixColoR) #remotes::install_github("johannesbjork/LaCroixColoR")
+my_pal <- lacroix_palette("PeachPear", n = 15, type = "continuous")
+my_pal <- rev(my_pal)
+
+# AM1 Cor Plot
 AM1_cor <- cor_df %>%
@@
     outline.col = "white",
-    colors = c("#6D9EC1", "white", "#E46726"),
+    colors = c(my_pal[1], "white", my_pal[15]),
     lab = TRUE,
+    sig.level = 0.05,
     insig = "blank",
@@
 
+# PDM10 Cor Plot
 PDM10_cor <- cor_df %>%
@@
     outline.col = "white",
-    colors = c("#6D9EC1", "white", "#E46726"),
+    colors = c(my_pal[1], "white", my_pal[15]),
     lab = TRUE,
@@
 
-rm(AM1_cor, PDM10_cor, cog_table, speaker_intel)
+rm(AM1_cor, PDM10_cor, cog_table, speaker_intel, demo_table)
 
@@
 
+### AM1 Models
+
 ```{r}
@@
          title = {{title}}) +
-    scale_color_viridis_c(option = "magma", end = .8) +
+    scale_color_gradientn(colors = my_pal) +
+    theme_bw() +
     theme(plot.title.position = "plot")
@@
 mods1 = mod_fun("AM1", "pretest")
-mods2 = mod_fun("PDM10", "pretest")
-
 p1 = plot_fun(mods1, "a) Ataxic")
-p2 = plot_fun(mods2, "b) PD")
-
-```
-
-```{r}
-
-p2
+p1
 
@@
 
-PDM10_initial_mod <- in_and_out(mods2, "PD")
-
-initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)
-
-initial_mods %>%
+AM1_initial_mod %>%
   gt::gt() %>%
@@
 t_for_diff(mods1)
-t_for_diff(mods2)
 
@@
 
+```
+
+### PDM10 Models
+
+```{r}
+
+mods2 = mod_fun("PDM10", "pretest")
+p2 = plot_fun(mods2, "b) PD")
+p2
+
+```
+
+```{r}
+
+PDM10_initial_mod <- in_and_out(mods2, "PD")
+
+```
+
+```{r}
+
 # PDM10 Effect Plots
@@
 ## Models of Cognition and Intelligibility Change
+
+### AM1 Models
 
@@
 mods12 = mod_fun2("AM1")
-mods22 = mod_fun2("PDM10")
-
 p12 = plot_fun(mods12, "a) Ataxic")
-p22 = plot_fun(mods22, "b) PD")
-
 p12
-```
-
-```{r}
-
-p22
 
@@
 
-PDM10_change_mod <- in_and_out(mods22, "PD")
-
-change_mods <- rbind(AM1_change_mod, PDM10_change_mod)
-
-change_mods %>%
+AM1_change_mod %>%
   gt::gt() %>%
@@
 t_for_diff(mods12)
-t_for_diff(mods22)
 
@@
 
+```
+
+### PDM10 Models
+
+```{r}
+
+mods22 = mod_fun2("PDM10")
+p22 = plot_fun(mods22, "b) PD")
+p22
+
+```
+
+```{r}
+
+PDM10_change_mod <- in_and_out(mods22, "PD")
+
+PDM10_change_mod %>%
+  gt::gt() %>%
+  cols_label(speaker = "Speaker",
+             mods = "Model Specification",
+             out_sample_r2 = "R\U00B2",
+             out_sample_rmse = "RMSE")
+
+```
+
+```{r}
+
+t_for_diff(mods22)
+
+```
+
+```{r}
+
 ## PDM10 Effect Plots
@@
 ```
+
+```{r, echo = F, warning = F, message = F}
+
+initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)
+
+mods_table %>%
+  gt::gt() %>%
+  cols_label(speaker = "Speaker",
+             mods = "Model Specification",
+             out_sample_r2 = "R\U00B2",
+             out_sample_rmse = "RMSE")
+
+change_mods <- rbind(AM1_change_mod, PDM10_change_mod)
+
+change_mods %>%
+  gt::gt() %>%
+  cols_label(speaker = "Speaker",
+             mods = "Model Specification",
+             out_sample_r2 = "R\U00B2",
+             out_sample_rmse = "RMSE")
+
+```

### 2024-01-04 Manuscript Analyses/manuscript_analysis.Rmd
formatting rmd file

@@
 
-rm(demo)
+rm(demo, demo_table)
 
@@
 
-rm(AM1_cor, PDM10_cor, cog_table, speaker_intel, demo_table)
+rm(AM1_cor, PDM10_cor, cog_table, speaker_intel)
 
@@
 
-effect_plot(mods1, pic_seq_c, best_win)
-effect_plot(mods1, best_win, pic_seq_c)
-effect_plot(mods1, best_win, int = F)
-effect_plot(mods1, list_sort_c, vocab_c)
-effect_plot(mods1, vocab_c, list_sort_c)
-effect_plot(mods1, list_sort_c, pattern_c)
-effect_plot(mods1, pattern_c, list_sort_c)
+effect_plot(mods1, pic_seq_c, best_win) # Picture Sequence Memory * Words in Noise
+effect_plot(mods1, best_win, pic_seq_c) # Words in Noise * Picture Sequence Memory
+effect_plot(mods1, best_win, int = F) # Words in Noise
+effect_plot(mods1, list_sort_c, vocab_c) # Working Memory * Receptive Vocab
+effect_plot(mods1, vocab_c, list_sort_c) # Receptive Vocab * Working Memory
+effect_plot(mods1, list_sort_c, pattern_c) # Working Memory * Processing Speed
+effect_plot(mods1, pattern_c, list_sort_c) # Processing Speed * Working Memory
 
@@
 
+PDM10_initial_mod %>%
+  gt::gt() %>%
+  cols_label(speaker = "Speaker",
+             mods = "Model Specification",
+             out_sample_r2 = "R\U00B2",
+             out_sample_rmse = "RMSE")
+
 ```
@@
 
-effect_plot(mods2, vocab_c, pattern_c)
-effect_plot(mods2, pattern_c, vocab_c)
-effect_plot(mods2, best_win, int = F)
-effect_plot(mods2, flanker_c, best_win)
-effect_plot(mods2, best_win, flanker_c)
-effect_plot(mods2, list_sort_c, pattern_c)
-effect_plot(mods2, pattern_c, list_sort_c)
-effect_plot(mods2, vocab_c, pic_seq_c)
-effect_plot(mods2, pic_seq_c, vocab_c)
-effect_plot(mods2, card_sort_c, vocab_c)
-effect_plot(mods2, vocab_c, card_sort_c)
+effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocab * Processing Speed
+effect_plot(mods2, pattern_c, vocab_c) # Processing Speed * Receptive Vocab
+effect_plot(mods2, best_win, int = F) # Words in Noise
+effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise
+effect_plot(mods2, best_win, flanker_c) # Words in Noise * Inhibitory Control
+effect_plot(mods2, list_sort_c, pattern_c) # Working Memory * Processing Speed
+effect_plot(mods2, pattern_c, list_sort_c) # Processing Speech * Working Memory
+effect_plot(mods2, vocab_c, pic_seq_c) # Receptive Vocab * Picture Sequence Memory
+effect_plot(mods2, pic_seq_c, vocab_c) # Picture Sequence Memory * Receptive Vocab
+effect_plot(mods2, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocab
+effect_plot(mods2, vocab_c, card_sort_c) # Receptive Vocab * Cognitive Flexibility
+
+```
+
+```{r, echo = F, warning = F, message = F}
+
+# Mergining initial model summaries together
+initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)
+
+# Combining initial model figures and saving
+p1 / p2
+ggsave("Plots/Initial_mods.png", plot = last_plot(), width = 8, height = 10, units = "in")
+
+# Removing unneeded items from Environment
+rm(p1, p2, mods1, mods2, AM1_initial_mod, PDM10_initial_mod)
 
@@
 
-effect_plot(mods12, list_sort_c, vocab_c)
-effect_plot(mods12, vocab_c, list_sort_c)
-effect_plot(mods12, list_sort_c, int = F)
-effect_plot(mods12, pattern_c, int = F)
-effect_plot(mods12, list_sort_c, flanker_c)
-effect_plot(mods12, flanker_c, list_sort_c)
+effect_plot(mods12, list_sort_c, vocab_c) # Working Memory * Receptive Vocab
+effect_plot(mods12, vocab_c, list_sort_c) # Receptive Vocab * Working Memory
+effect_plot(mods12, list_sort_c, int = F) # Working Memory
+effect_plot(mods12, pattern_c, int = F) # Processing Speed
+effect_plot(mods12, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
+effect_plot(mods12, flanker_c, list_sort_c) # Inhibitory Control * Working Memory
 
@@
 
-effect_plot(mods22, vocab_c, pic_seq_c)
-effect_plot(mods22, pic_seq_c, vocab_c)
-effect_plot(mods22, vocab_c, int = F)
-effect_plot(mods22, list_sort_c, flanker_c)
-effect_plot(mods22, flanker_c, list_sort_c)
+effect_plot(mods22, vocab_c, pic_seq_c) # Receptive Vocab * Picture Sequence Memory
+effect_plot(mods22, pic_seq_c, vocab_c) # Picture Sequence Memory * Receptive Vocab
+effect_plot(mods22, vocab_c, int = F) # Receptive Vocab
+effect_plot(mods22, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
+effect_plot(mods22, flanker_c, list_sort_c) # Inhibitory Control * Working Memory
+
+```
+
+```{r}
+
+# Merging Model summaries together
+change_mods <- rbind(AM1_change_mod, PDM10_change_mod)
+
+# Combining and saving change model figures
+p12 / p22
+ggsave("Plots/Change_mods.png", plot = last_plot(), width = 8, height = 10, units = "in")
+
+# Removing unneeded items from environment
+rm(p12, p22, AM1_change_mod, PDM10_change_mod, mods12, mods22)
 
@@
 
-initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)
+# Creating Overall Model Table
+
+initial_mods <- initial_mods %>%
+  dplyr::mutate(outcome = "Initial Intelligibility")
+
+change_mods <- change_mods %>%
+  dplyr::mutate(outcome = "Intelligbility Change")
+
+mods_table <- rbind(initial_mods, change_mods)
 
 mods_table %>%
-  gt::gt() %>%
+  gt::gt(groupname_col = "outcome") %>%
   cols_label(speaker = "Speaker",
@@
              out_sample_r2 = "R\U00B2",
-             out_sample_rmse = "RMSE")
-
-change_mods <- rbind(AM1_change_mod, PDM10_change_mod)
-
-change_mods %>%
-  gt::gt() %>%
-  cols_label(speaker = "Speaker",
-             mods = "Model Specification",
-             out_sample_r2 = "R\U00B2",
-             out_sample_rmse = "RMSE")
+             out_sample_rmse = "RMSE") %>%
+  gt::gtsave("Tables/mods_table.html")
 

### 2024-01-04 Manuscript Analyses/manuscript_analysis.Rmd
Knit draft rmd report

@@
 output: 
-  github_document:
+  html_document:
     code_folding: hide

### 2024-01-05 Manuscript Analyses/manuscript_analysis.Rmd
Added Initial PD model comparison
Added additional corr matricies

@@
 
-First, pretest and posttest intelligibility was calculated as percent words correct (pwc) for each listener.
+First, pretest and posttest intelligibility was calculated as a percent words correct (pwc) score for each listener.
+Pretest PWC and PWC change (posttest-pretest) will be our outcome variables for the analyses.
 
@@
 
-A total of 60 older adult listeners participated in the study. The overall demographic information for the participants are below.
+A total of 60 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
 
@@
 
+Words in noise significantly correlated with pretest intelligibility for AM1 at the alpha = 0.05 level.
+Listeners with higher (i.e.
+worse) words in noise hearing thresholds tend to have lower pretest intelligibility (i.e.
+lower initial intelligibility) for AM1.
+
 ```{r, warning = F, message = F}
@@
     lab = TRUE,
-    sig.level = 0.05,
     insig = "blank",
@@
 
+The plot below shows only the significant correlations in the matrix above for AM1.
+
+```{r, warning = F, message = F}
+
+cor_df %>%
+  dplyr::filter(speaker == "AM1") %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Picture Sequence Memory` = pic_seq_c,
+    `Words in Noise Threshold` = best_win
+  ) %>%
+  dplyr::rename_all(snakecase::to_title_case) %>%
+  cor(use = "pairwise.complete.obs") %>%
+  ggcorrplot(
+    type = "lower",
+    outline.col = "white",
+    colors = c(my_pal[1], "white", my_pal[15]),
+    lab = TRUE,
+    p.mat = cor_pmat(.),
+    sig.level = 0.05,
+    insig = "blank",
+    title = "Ataxic", 
+    legend.title = "Correlation"
+  )
+
+```
+
 ### PDM10
+
+Like AM1, words in noise hearing threshold significantly correlated with pretest intelligibility.
+However, listener processing speed has a weak, but significant, correlation with intelligibility improvement.
+Pretest intelligibility is also has a negative correlation with intelligibility improvement, indicating that listeners in this group who had higher pretest intelligibility tend to have less intelligibility gains at posttest.
 
@@
 
-```{r, echo = F, warning = F, message = F}
+The plot below only shows the significant correlations for PDM10.
+
+```{r}
+
+cor_df %>%
+  dplyr::filter(speaker == "PDM10") %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Picture Sequence Memory` = pic_seq_c,
+    `Words in Noise Threshold` = best_win
+  ) %>%
+  dplyr::rename_all(snakecase::to_title_case) %>%
+  cor(use = "pairwise.complete.obs") %>%
+  ggcorrplot(
+    type = "lower",
+    outline.col = "white",
+    colors = c(my_pal[1], "white", my_pal[15]),
+    lab = TRUE,
+    p.mat = cor_pmat(.),
+    insig = "blank",
+    sig.level = 0.05,
+    title = "Parkinson's Disease", 
+    legend.title = "Correlation"
+  )
+
+```
+
+```{r, eval = F, warning = F, message = F}
 
@@
 ```{r}
+t_for_diff(mods2)
+```
+
+```{r}
 

### 2024-01-05 Manuscript Analyses/manuscript_analysis.Rmd
Cleaning code and formatting rmd

@@
 However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10.
-A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p < .001, d = 1.01).
+A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p \< .001, d = 1.01).
 
@@
 
-```{r, eval = F, warning = F, message = F}
+```{r, echo = F, warning = F, message = F}
 
@@
 
-```{r}
+Two elastic net models were conducted to evaluate the predictive relationship between the cognitive measures on pretest (initial) intelligibility: A model containing only the main effects of the cognitive measures (i.e.
+the main effects model) and another model that contains the main effects and all two-way interactions (i.e.
+the interaction model).
+The cross-validated R-squared and RMSE values are not significantly different between these two models.
+
+The relative variable importance for the models are shown in the figure below.
+The interaction between episodic (picture sequence) memory and words in noise hearing threshold, the main effect of words in noise threshold, the interaction between working memory and receptive vocabulary, and the interaction between working memory and processing speed were the most important variables for the AM1 initial intelligibility models.
+
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+Plotting the interaction effects for the AM1 initial intelligibility models.
+
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+Like for AM1, two elastic net models were used to model the predictive relationship between the listener cognitive measures and pretest intelligibility for PDM10: a main effects model and an interaction model.
+The difference in R-square and RMSE is not significantly different between the two models.
+However, the R-squared value is higher for the main effects model, indicating a better fit to the data.
+
+The important variables for the PDM10 models is shown below.
+The interaction between receptive vocabulary and processing speed, the main efffect of words in noise hearing threshold, the interaction between inhibitory control and words in noise hearing threshold, and the interaction between working memory and processing speed were the most important variables in the models (in that order).
+
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+```{r, warning = F, message = F}
 t_for_diff(mods2)
@@
 
-# Mergining initial model summaries together
+# Merging initial model summaries together
 initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)
@@
 
-```{r}
+Two elastic net models were used to model the relationship between the listener cognitive measures and intelligibility improvement (controlling for pretest intelligibility) for AM1: the main effects only model and the model with interactions.
+Based on the R-squared values, the main effects model is better than the interaction model (this difference approached significance).
+
+The relative importance of the model variables are shown in the figure below.
+
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+```{r warning = F, message = F}
 
@@
 ```
+
+Plotting the interaction effects for intelligibility improvement models for AM1.
 
@@
 
-```{r}
+Two elastic net models were used to model the relationships between listener cognition measures and intelligibility improvement (controlling for pretest intelligibility) for PDM10.
+There is not a significant difference between the R-squared values for the two models.
+
+The relative importance of the model variables is shown in the figure below.
+
+```{r, warning = F, message = F}
 
@@
 
-```{r}
+Plotting the interaction effects for the intelligibility improvement models for PDM10.
+
+```{r, warning = F, message = F}
 
@@
 
-```{r, echo = F, warning = F, message = F}
-
-# Merging Model summaries together
-change_mods <- rbind(AM1_change_mod, PDM10_change_mod)
+```{r, eval = F, warning = F, message = F}
 
@@
 
-# Removing unneeded items from environment
-rm(p12, p22, AM1_change_mod, PDM10_change_mod, mods12, mods22)
-
 ```
@@
 ```{r, echo = F, warning = F, message = F}
+
+# Merging Model summaries together
+change_mods <- rbind(AM1_change_mod, PDM10_change_mod)
 
@@
 
+# Removing unneeded items from environment
+rm(p12, p22, AM1_change_mod, PDM10_change_mod, mods12, mods22)
+
 ```

### 2024-01-08 Manuscript Analyses/manuscript_analysis.Rmd
Small rmd edits
removed episodic mem from analysis

@@
   dplyr::select(id, speaker, age, ends_with("_c"), best_win) %>%
-  dplyr::select(-fluid_cog_c) %>%
+  dplyr::select(-c(fluid_cog_c, pic_seq_c)) %>%
   dplyr::rename(
@@
     `Processing Speed` = pattern_c,
-    `Picture Sequence Memory` = pic_seq_c,
     `Words in Noise Threshold` = best_win
@@
 However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10.
-A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p \< .001, d = 1.01).
+A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p < .001, d = 1.01).
 
@@
   dplyr::filter(speaker == "AM1") %>%
-  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c, pic_seq_c, posttest)) %>%
   dplyr::rename(
@@
 Like AM1, words in noise hearing threshold significantly correlated with pretest intelligibility.
-However, listener processing speed has a weak, but significant, correlation with intelligibility improvement.
-Pretest intelligibility is also has a negative correlation with intelligibility improvement, indicating that listeners in this group who had higher pretest intelligibility tend to have less intelligibility gains at posttest.
+However, pretest intelligibility is also has a negative correlation with intelligibility improvement, indicating that listeners in this group who had higher pretest intelligibility tend to have less intelligibility gains at posttest.
 
@@
   dplyr::filter(speaker == "PDM10") %>%
-  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
+  dplyr::select(!c(id, speaker, fluid_cog_c, pic_seq_c, posttest)) %>%
   dplyr::rename(
@@
 
-```{r, echo = F, warning = F, message = F}
+```{r, eval = F, warning = F, message = F}
 
@@
 ggsave("Plots/cor_fig.png", width = 20, height = 6, dpi = 300, units = "in")
+
+```
+
+```{r, echo = F, warning = F, message = F}
 
@@
 The cross-validated R-squared and RMSE values are not significantly different between these two models.
+However, the r-squared value for the main effects model is higher.
 
 The relative variable importance for the models are shown in the figure below.
-The interaction between episodic (picture sequence) memory and words in noise hearing threshold, the main effect of words in noise threshold, the interaction between working memory and receptive vocabulary, and the interaction between working memory and processing speed were the most important variables for the AM1 initial intelligibility models.
+The most important predictor for the AM1 initial intelligibility model was words-in-noise hearing threshold, followed by working memory, the interaction between working memory and inhibitory control, and the interaction between working memory and receptive vocabulary.
 
@@
     drop_na(pwc, ends_with("_c"), best_win) %>% 
-    select(-contains("fluid"))
+    select(-c(fluid_cog_c, pic_seq_c))
 
@@
            var = str_replace(var, "card_sort_c", "Cognitive Flexibility"),
-           var = str_replace(var, "vocab_c", "Vocabulary Knowledge"),
+           var = str_replace(var, "vocab_c", "Receptive Vocabulary"),
            var = str_replace(var, "pattern_c", "Processing Speed"),
            var = str_replace(var, "list_sort_c", "Working Memory"),
-           var = str_replace(var, "pic_seq_c", "Picture Sequence Memory"),
            var = str_replace(var, "best_win", "Words in Noise Threshold"),
@@
 
-effect_plot(mods1, pic_seq_c, best_win) # Picture Sequence Memory * Words in Noise
-effect_plot(mods1, best_win, pic_seq_c) # Words in Noise * Picture Sequence Memory
 effect_plot(mods1, best_win, int = F) # Words in Noise
+effect_plot(mods1, list_sort_c, int = F) # Working Memory
+effect_plot(mods1, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
+effect_plot(mods1, flanker_c, list_sort_c) # Inhibitory Control * Working Memory
 effect_plot(mods1, list_sort_c, vocab_c) # Working Memory * Receptive Vocab
 effect_plot(mods1, vocab_c, list_sort_c) # Receptive Vocab * Working Memory
-effect_plot(mods1, list_sort_c, pattern_c) # Working Memory * Processing Speed
-effect_plot(mods1, pattern_c, list_sort_c) # Processing Speed * Working Memory
 
@@
 The difference in R-square and RMSE is not significantly different between the two models.
-However, the R-squared value is higher for the main effects model, indicating a better fit to the data.
+However, the R-squared value is higher for the interaction model, indicating a better fit to the data.
 
 The important variables for the PDM10 models is shown below.
-The interaction between receptive vocabulary and processing speed, the main efffect of words in noise hearing threshold, the interaction between inhibitory control and words in noise hearing threshold, and the interaction between working memory and processing speed were the most important variables in the models (in that order).
+The interaction between working memory and words in noise hearing threshold is the most important predictor, followed by the main effect of words in noise hearing threshold, the interaction between working memory and receptive vocabulary, the interaction between cognitive flexibility and processing speed, the interaction between inhibiotry control and words in noise hearing threshold, the interaction between receptive vocabulary and processing speed, and the interaction between working memory and cognitive flexibility.
 
@@
 
-effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocab * Processing Speed
-effect_plot(mods2, pattern_c, vocab_c) # Processing Speed * Receptive Vocab
-effect_plot(mods2, best_win, int = F) # Words in Noise
-effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise
-effect_plot(mods2, best_win, flanker_c) # Words in Noise * Inhibitory Control
-effect_plot(mods2, list_sort_c, pattern_c) # Working Memory * Processing Speed
-effect_plot(mods2, pattern_c, list_sort_c) # Processing Speech * Working Memory
-effect_plot(mods2, vocab_c, pic_seq_c) # Receptive Vocab * Picture Sequence Memory
-effect_plot(mods2, pic_seq_c, vocab_c) # Picture Sequence Memory * Receptive Vocab
-effect_plot(mods2, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocab
-effect_plot(mods2, vocab_c, card_sort_c) # Receptive Vocab * Cognitive Flexibility
+effect_plot(mods2, list_sort_c, best_win) # Working Memory * Words in Noise Threshold
+effect_plot(mods2, best_win, list_sort_c) # Words in Noise Threshold * Working Memory
+effect_plot(mods2, best_win, int = F) # Words in Noise Threshold
+effect_plot(mods2, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
+effect_plot(mods2, card_sort_c, pattern_c) # Cognitive Flexibility * Processing Speed
+effect_plot(mods2, pattern_c, card_sort_c) # Processing Speed * Cognitive Flexibility
+effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
+effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocabulary * Processing Speed
+effect_plot(mods2, pattern_c, vocab_c) # Processing Speed * Receptive Vocabulary
+effect_plot(mods2, list_sort_c, card_sort_c) # Working Memory * Cognitive Flexibility
+effect_plot(mods2, card_sort_c, list_sort_c) # Cognitive Flexibility * Working Memory
+
+```
+
+```{r, eval = F, warning = F, message = F}
+
+# Combining initial model figures and saving
+p1 / p2
+ggsave("Plots/Initial_mods.png", plot = last_plot(), width = 8, height = 10, units = "in")
 
@@
 initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)
-
-# Combining initial model figures and saving
-p1 / p2
-ggsave("Plots/Initial_mods.png", plot = last_plot(), width = 8, height = 10, units = "in")
 
@@
 Two elastic net models were used to model the relationship between the listener cognitive measures and intelligibility improvement (controlling for pretest intelligibility) for AM1: the main effects only model and the model with interactions.
-Based on the R-squared values, the main effects model is better than the interaction model (this difference approached significance).
 
@@
   subsetted = cor_df %>%
-    dplyr::select(-c(fluid_cog_c, improvement)) %>%
+    dplyr::select(-c(fluid_cog_c, pic_seq_c, improvement)) %>%
     dplyr::mutate(pwc_diff = resid(lm(posttest ~ pretest))) %>%
@@
 
-effect_plot(mods12, list_sort_c, vocab_c) # Working Memory * Receptive Vocab
-effect_plot(mods12, vocab_c, list_sort_c) # Receptive Vocab * Working Memory
+effect_plot(mods12, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
+effect_plot(mods12, vocab_c, list_sort_c) # Receptive Vocabulary * Working Memory
 effect_plot(mods12, list_sort_c, int = F) # Working Memory
@@
 
-effect_plot(mods22, vocab_c, pic_seq_c) # Receptive Vocab * Picture Sequence Memory
-effect_plot(mods22, pic_seq_c, vocab_c) # Picture Sequence Memory * Receptive Vocab
 effect_plot(mods22, vocab_c, int = F) # Receptive Vocab 
-effect_plot(mods22, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
-effect_plot(mods22, flanker_c, list_sort_c) # Inhibitory Control * Working Memory
+effect_plot(mods22, flanker_c, int = F) # Inhibitory Control
+effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocab
 
@@
              out_sample_rmse = "RMSE") %>%
+  fmt_number(decimals = 2) %>%
   gt::gtsave("Tables/mods_table.html")

### 2024-01-10 Manuscript Analyses/manuscript_analysis.Rmd
Added best_win to intel change models

@@
 ```{r, warning = F, message = F}
+
+# Removing Participant 323 from the dataset (missing demographic and cognitive data)
+
+data <- data %>%
+  dplyr::filter(id != 323)
+
+demo <- demo %>%
+  dplyr::filter(id != 323)
 
@@
 The important variables for the PDM10 models is shown below.
-The interaction between working memory and words in noise hearing threshold is the most important predictor, followed by the main effect of words in noise hearing threshold, the interaction between working memory and receptive vocabulary, the interaction between cognitive flexibility and processing speed, the interaction between inhibiotry control and words in noise hearing threshold, the interaction between receptive vocabulary and processing speed, and the interaction between working memory and cognitive flexibility.
+The interaction between working memory and words in noise hearing threshold is the most important predictor, followed by the main effect of words in noise hearing threshold, the interaction between working memory and receptive vocabulary, the interaction between cognitive flexibility and processing speed, the interaction between inhibitory control and words in noise hearing threshold, the interaction between receptive vocabulary and processing speed, and the interaction between working memory and cognitive flexibility.
 
@@
 
-Plotting the interaction effects for the AM1 initial intelligibility models.
+Plotting the interaction effects for the PDM10 initial intelligibility models.
 
@@
 The relative importance of the model variables are shown in the figure below.
+The most important variable in the model is the interaction between inhibitory control and words in noise hearing threshold followed by the interaction between processing speed and words in noise threshold, the interaction between cognitive flexibility and words in noise hearing threshold, and the interaction between inhibitory control and receptive vocabulary.
 
@@
     dplyr::mutate(pwc_diff = resid(lm(posttest ~ pretest))) %>%
-    dplyr::select(pwc_diff, ends_with("_c"), speaker) %>%
-    tidyr::drop_na(pwc_diff, ends_with("_c"), speaker) %>%
+    dplyr::select(pwc_diff, ends_with("_c"), speaker, best_win) %>%
+    tidyr::drop_na(pwc_diff, ends_with("_c"), speaker, best_win) %>%
     dplyr::filter(speaker == {{speaker}}) %>%
@@
 
-effect_plot(mods12, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
-effect_plot(mods12, vocab_c, list_sort_c) # Receptive Vocabulary * Working Memory
-effect_plot(mods12, list_sort_c, int = F) # Working Memory
-effect_plot(mods12, pattern_c, int = F) # Processing Speed
-effect_plot(mods12, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
-effect_plot(mods12, flanker_c, list_sort_c) # Inhibitory Control * Working Memory
+effect_plot(mods12, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
+effect_plot(mods12, pattern_c, best_win) # Processing Speed * Words in Noise Threshold
+effect_plot(mods12, card_sort_c, best_win) # Cognitive Flexibility * Words in Noise Threshold
+effect_plot(mods12, flanker_c, vocab_c) # Inhibitory Control * Receptive Vocabulary
+effect_plot(mods12, vocab_c, flanker_c) # Receptive Vocabulary * Inhibitory Control
 
@@
 The relative importance of the model variables is shown in the figure below.
+The most important variable in the model is the interaction between cognitive flexibility and receptive vocabulary followed by the interaction between inhibitory control and processing speed, the main effect of receptive vocabulary, the main effect of inhibitory control, and the interaction between inhibitory control and words in noise hearing threshold.
 
@@
 
+effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
+effect_plot(mods22, vocab_c, card_sort_c) # Receptive Vocabulary * Cognitive Flexibility
+effect_plot(mods22, flanker_c, pattern_c) # Inhibitory Control * Processing Speed
+effect_plot(mods22, pattern_c, flanker_c) # Processing Speed * Inhibitory Control
 effect_plot(mods22, vocab_c, int = F) # Receptive Vocab 
 effect_plot(mods22, flanker_c, int = F) # Inhibitory Control
-effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocab
+effect_plot(mods22, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
+effect_plot(mods22, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
 

### 2024-01-10 Manuscript Analyses/manuscript_analysis.Rmd
updated effects plot function

@@
           y= .outcome,
-          group = cut_interval({{var2}}, num),
-          color = cut_interval({{var2}}, num)) +
+          group = cut_number({{var2}}, num),
+          color = cut_number({{var2}}, num)) +
       geom_point() +
@@
 effect_plot(mods2, list_sort_c, best_win) # Working Memory * Words in Noise Threshold
-effect_plot(mods2, best_win, list_sort_c) # Words in Noise Threshold * Working Memory
+#effect_plot(mods2, best_win, list_sort_c) # Words in Noise Threshold * Working Memory
 effect_plot(mods2, best_win, int = F) # Words in Noise Threshold
 effect_plot(mods2, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
+effect_plot(mods2, vocab_c, list_sort_c)
 effect_plot(mods2, card_sort_c, pattern_c) # Cognitive Flexibility * Processing Speed
@@
 
-effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
+# effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
 effect_plot(mods22, vocab_c, card_sort_c) # Receptive Vocabulary * Cognitive Flexibility

### 2024-01-16 Manuscript Analyses/manuscript_analysis.Rmd
reran analyses

@@
 
-speaker_intel <- pl_int %>%
-  dplyr::mutate(type = as.factor(type),
-                type = fct_relevel(type, "pretest", "posttest")) %>%
-  dplyr::group_by(speaker, type) %>%
-  dplyr::summarize(m_pwc = mean(pwc),
-                   sd_pwc = sd(pwc)) %>%
-  dplyr::ungroup() %>%
-  tidyr::pivot_wider(names_from = speaker,
-                     values_from = c(m_pwc:sd_pwc)) %>%
-  dplyr::relocate(sd_pwc_AM1, .after = m_pwc_AM1) %>%
-  gt::gt() %>%
-    fmt_number(columns = "m_pwc_AM1":"sd_pwc_PDM10", decimals = 2) %>%
-    tab_spanner(label = "AM1",
-                columns = c(m_pwc_AM1, sd_pwc_AM1)) %>%
-    tab_spanner(label = "PDM10",
-                columns = c(m_pwc_PDM10, sd_pwc_PDM10)) %>%
-    cols_label(type = " ",
-               m_pwc_AM1 = "Mean",
-               sd_pwc_AM1 = "SD",
-               m_pwc_PDM10 = "Mean",
-               sd_pwc_PDM10 = "SD")
+speaker_intel <- cor_df %>%
+  dplyr::select(speaker, pretest, posttest, improvement) %>%
+  tbl_summary(
+    by = speaker,
+    statistic = list(all_continuous() ~ "{mean} ({sd})"),
+    missing = "no",
+    digits = list(everything() ~ c(2)),
+    label = list(pretest ~ "Pretest Inelligibility",
+                   posttest ~ "Posttest Intelligibility",
+                   improvement ~ "Intelligibility Change")) %>%
+  as_gt()
 
@@
 
+# Customize colors for figures
+library(LaCroixColoR) #remotes::install_github("johannesbjork/LaCroixColoR")
+my_pal <- lacroix_palette("PeachPear", type = "discrete")
+
 pl_int %>%
@@
       y = pwc,
-      group = id) +
+      group = id,
+      color = speaker) +
   geom_line(alpha = 0.3) +
+  geom_point(alpha = 0.3) +
   stat_summary(aes(group = speaker),
@@
   theme_classic() +
+  scale_color_manual(values = c(my_pal[5], my_pal[6])) +
   theme(legend.position = "none", aspect.ratio = 1)
@@
 # Customize plot colors
-
-library(LaCroixColoR) #remotes::install_github("johannesbjork/LaCroixColoR")
 my_pal <- lacroix_palette("PeachPear", n = 15, type = "continuous")
@@
 However, the r-squared value for the main effects model is higher.
+Therefore, the main effects model is the best model for the AM1 initial intelligibility model.
 
 The relative variable importance for the models are shown in the figure below.
-The most important predictor for the AM1 initial intelligibility model was words-in-noise hearing threshold, followed by working memory, the interaction between working memory and inhibitory control, and the interaction between working memory and receptive vocabulary.
+The most important predictor for the AM1 initial intelligibility model was words-in-noise hearing threshold, followed by the main effect of working memory.
 
@@
 
-Plotting the interaction effects for the AM1 initial intelligibility models.
+The plots below are showing the effects of words in noise hearing threshold and working memory on initial intelligibility for AM1.
+
+-   Words in Noise Hearing Threshold has a negative relationship with initial intelligibility, indicating that those with higher words in noise thresholds have lower initial intelligibility for AM1.
+-   Working Memory has a positive relationship with initial intelligibility, indicating that those listeners with greater working memory capacity had higher initial intelligibility for AM1.
 
@@
 effect_plot(mods1, list_sort_c, int = F) # Working Memory
-effect_plot(mods1, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
-effect_plot(mods1, flanker_c, list_sort_c) # Inhibitory Control * Working Memory
-effect_plot(mods1, list_sort_c, vocab_c) # Working Memory * Receptive Vocab
-effect_plot(mods1, vocab_c, list_sort_c) # Receptive Vocab * Working Memory
 
@@
 The difference in R-square and RMSE is not significantly different between the two models.
-However, the R-squared value is higher for the interaction model, indicating a better fit to the data.
+However, the R-squared value is higher for the interaction model and multiple interactions were indicated as important predictors.
 
@@
 
-Plotting the interaction effects for the PDM10 initial intelligibility models.
+The figures below are plotting the interaction effects for the PDM10 initial intelligibility models.
+
+-   The interaction between working memory and words in noise hearing threshold indicates that working memory did not have much of an effect for listeners with lower (i.e.
+better) hearing thresholds on initial intelligibility for PDM10.
+However, working memory help compensate for listeners with elevated hearing thresholds.
+-   Like with AM1, words in noise hearing threshold has a negative relationship with initial intelligibility for PDM10. 
+-   The interaction between working memory and receptive vocabulary indicates that greater receptive vocabulary knowledge helped compensate for listeners with lower working memory capacity. 
+-   The interaction between cognitive flexibility and processing speech indicates that greater cognitive flexibility helped compensate for listener with lower processing speed.
+However, greater processing speed tends to have a negative effect on initial intelligibility for listeners with greater cognitive flexibility.
+-   The interaction between inhibitory control and words in noise hearing threshold indicate that inhibitory control helped compensate for listeners with slightly elevated words in noise hearing thresholds.
+However, inhibitory control did not have a great effect on initial intelligibility for listeners with low or elevated hearing thresholds.
+-   The interaction between receptive vocabulary and processing speed indicates that those with greater processing speed and greater vocabulary had greater initial intelligibility
+-   The interaction between cognitive flexibility and working memory indicates that cognitive flexibility helps compensate perception for listeners with lower working memory capacity, but may not have much of an effect (or even a possible negative effect) for listeners with higher working memory capacity.
 
@@
 effect_plot(mods2, list_sort_c, best_win) # Working Memory * Words in Noise Threshold
-#effect_plot(mods2, best_win, list_sort_c) # Words in Noise Threshold * Working Memory
 effect_plot(mods2, best_win, int = F) # Words in Noise Threshold
-effect_plot(mods2, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
-effect_plot(mods2, vocab_c, list_sort_c)
+effect_plot(mods2, vocab_c, list_sort_c) # Receptive Vocabulary * Working Memory
 effect_plot(mods2, card_sort_c, pattern_c) # Cognitive Flexibility * Processing Speed
@@
 effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
+effect_plot(mods2, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
 effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocabulary * Processing Speed
@@
 Two elastic net models were used to model the relationship between the listener cognitive measures and intelligibility improvement (controlling for pretest intelligibility) for AM1: the main effects only model and the model with interactions.
+The difference in RMSE and R-squared is not significantly different.
+However, multiple interactions were indicated to be important predictors in the model.
 
@@
 
-Plotting the interaction effects for intelligibility improvement models for AM1.
+The the interaction effects for the intelligibility improvement model for AM1 are plotted below.
+
+-   The interaction between inhibitory control and words in noise threshold indicate that the effect of inhibiotry control on intelligibility improvement was reduced for listeners with higher hearing thresholds
+-   The interaction between processing speed and words in noise threshold indicate that greater processing speed reduced the effect on intelligibility improvement for listeners with higher thresholds.***
+- The interaction between cognitive flexibility and words in noise threshold indicate that greater cognitive flexibility helped compensate for intelligibility improvement for listeners with high thresholds.
+However, for listeners with lower thresholds, greater cognitive flexibility had a negative effect on improvement.
+-   The interaction between inhibitory control and receptive vocabulary indicates that increased vocabulary knowledge had a positive effect on intelligibility improvement for listeners with low and high inhibitory control.
+However, vocabulary knowledge had a negative effect for listeners with "mid/average" inhibitory control.
 
@@
 effect_plot(mods12, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
-effect_plot(mods12, pattern_c, best_win) # Processing Speed * Words in Noise Threshold
-effect_plot(mods12, card_sort_c, best_win) # Cognitive Flexibility * Words in Noise Threshold
-effect_plot(mods12, flanker_c, vocab_c) # Inhibitory Control * Receptive Vocabulary
-effect_plot(mods12, vocab_c, flanker_c) # Receptive Vocabulary * Inhibitory Control
+effect_plot(mods12, best_win, flanker_c) # Words in Noise * Inhibitory Control
+effect_plot(mods12, pattern_c, best_win, num = 4) # Processing Speed * Words in Noise Threshold
+effect_plot(mods12, best_win, pattern_c, num = 4)
+effect_plot(mods12, card_sort_c, best_win, num = 5) # Cognitive Flexibility * Words in Noise Threshold
+effect_plot(mods12, flanker_c, vocab_c, num = 5) # Inhibitory Control * Receptive Vocabulary
+effect_plot(mods12, vocab_c, flanker_c, num = 5) # Receptive Vocabulary * Inhibitory Control
 
@@
 
-Plotting the interaction effects for the intelligibility improvement models for PDM10.
+The interaction effects for the intelligibility improvement models for PDM10 are plotted below.
+
+-   The interaction between cognitive flexibility and receptive vocabulary indicates that cognitive flexibility had a positive effect on improvement for listeners with higher vocabulary knowledge, but minimal effect for listeners with lower vocabulary knowledge
+-   The interaction effect between inhibitory control and processing speed indicates that processing speed has a negative effect on intelligibility improvement for listeners with mid-range inhibitory control.
+However, processing speed has minimal effect on improvement when listeners have lower or higher inhibitory control scores.***
+-   Receptive vocabulary has a positive effect on intelligibility improvement.
+-   Inhibitory control has a negative effect on intelligibility improvement.
+-   The interaction between inhibitory control and words in noise threshold indicates a positive effect of inhibitory control for listeners with low words in noise thresholds but little to no effect for listeners with elevated hearing thresholds (a potential negative effect)
 
@@
 
-# effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
+effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
 effect_plot(mods22, vocab_c, card_sort_c) # Receptive Vocabulary * Cognitive Flexibility
@@
 effect_plot(mods22, flanker_c, int = F) # Inhibitory Control
-effect_plot(mods22, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
-effect_plot(mods22, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
+effect_plot(mods22, flanker_c, best_win, num = 4) # Inhibitory Control * Words in Noise Threshold
 

### 2024-01-18 Manuscript Analyses/manuscript_analysis.Rmd
updated pre-post plot

@@
 library(LaCroixColoR) #remotes::install_github("johannesbjork/LaCroixColoR")
-my_pal <- lacroix_palette("PeachPear", type = "discrete")
+
+my_pal <- c("#782F40", "#B89751")
 
@@
   theme_classic() +
-  scale_color_manual(values = c(my_pal[5], my_pal[6])) +
+  scale_color_manual(values = my_pal) +
   theme(legend.position = "none", aspect.ratio = 1)

### 2024-01-18 Manuscript Analyses/manuscript_analysis.Rmd
Updated initial mod figures

@@
 
-The plots below are showing the effects of words in noise hearing threshold and working memory on initial intelligibility for AM1.
+## Interaction Effects
 
@@
 }
+
+```
+
+```{r, echo = F, warning = F, message = F}
 
@@
 
-The figures below are plotting the interaction effects for the PDM10 initial intelligibility models.
+## Interaction Effects
 
@@
 However, greater processing speed tends to have a negative effect on initial intelligibility for listeners with greater cognitive flexibility.
--   The interaction between inhibitory control and words in noise hearing threshold indicate that inhibitory control helped compensate for listeners with slightly elevated words in noise hearing thresholds.
-However, inhibitory control did not have a great effect on initial intelligibility for listeners with low or elevated hearing thresholds.
--   The interaction between receptive vocabulary and processing speed indicates that those with greater processing speed and greater vocabulary had greater initial intelligibility
+-   The interaction between inhibitory control and words in noise hearing threshold indicate that inhibitory control helped compensate for listeners with elevated words in noise hearing thresholds.
+However, inhibitory control did not have a great effect on initial intelligibility for listeners with lower hearing thresholds.
+-   The interaction between receptive vocabulary and processing speed indicates that those with greater processing speed and greater vocabulary had higher initial intelligibility scores for AM1.
+Processing speed also has a compensatory effect for listeners with lower receptive vocabulary knowledge.
+However, processing speed has minimal effect on initial intelligibility for listeners with average/mid-range receptive vocabulary knowledge.
 -   The interaction between cognitive flexibility and working memory indicates that cognitive flexibility helps compensate perception for listeners with lower working memory capacity, but may not have much of an effect (or even a possible negative effect) for listeners with higher working memory capacity.
 
-```{r, warning = F, message = F}
+```{r, eval = F, warning = F, message = F}
 
@@
 effect_plot(mods2, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
-effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocabulary * Processing Speed
-effect_plot(mods2, pattern_c, vocab_c) # Processing Speed * Receptive Vocabulary
+effect_plot(mods2, vocab_c, pattern_c, num = 4) # Receptive Vocabulary * Processing Speed
+effect_plot(mods2, pattern_c, vocab_c, num = 4) # Processing Speed * Receptive Vocabulary
 effect_plot(mods2, list_sort_c, card_sort_c) # Working Memory * Cognitive Flexibility

### 2024-01-18 Manuscript Analyses/manuscript_analysis.Rmd
updated change mod figures

@@
 
+# Alternative initial model figure
+
+p1 + p2
+ggsave("Plots/Initial_mods_wide.png", plot = last_plot(), width = 15, height = 5, units = "in")
+
 ```
@@
 The relative importance of the model variables are shown in the figure below.
-The most important variable in the model is the interaction between inhibitory control and words in noise hearing threshold followed by the interaction between processing speed and words in noise threshold, the interaction between cognitive flexibility and words in noise hearing threshold, and the interaction between inhibitory control and receptive vocabulary.
+The most important variable in the model is the interaction between inhibitory control and words in noise hearing threshold followed by the interaction between processing speed and words in noise threshold.
 
@@
 
-The the interaction effects for the intelligibility improvement model for AM1 are plotted below.
+## Interaction Effects
 
--   The interaction between inhibitory control and words in noise threshold indicate that the effect of inhibiotry control on intelligibility improvement was reduced for listeners with higher hearing thresholds
--   The interaction between processing speed and words in noise threshold indicate that greater processing speed reduced the effect on intelligibility improvement for listeners with higher thresholds.***
-- The interaction between cognitive flexibility and words in noise threshold indicate that greater cognitive flexibility helped compensate for intelligibility improvement for listeners with high thresholds.
-However, for listeners with lower thresholds, greater cognitive flexibility had a negative effect on improvement.
--   The interaction between inhibitory control and receptive vocabulary indicates that increased vocabulary knowledge had a positive effect on intelligibility improvement for listeners with low and high inhibitory control.
-However, vocabulary knowledge had a negative effect for listeners with "mid/average" inhibitory control.
+-   The interaction between inhibitory control and words in noise threshold indicate that listeners with lower hearing thresholds and higher inhibitory control had better intelligibility improvement for AM1.
+However, inhibitory control had minimal effects for listeners with elevated hearing thresholds.
+-   The interaction between processing speed and words in noise threshold indicate that greater processing speed has a negative effect on intelligibility improvement for listeners with higher hearing thresholds.
+***
 
-```{r, warning = F, message = F}
+```{r, eval = F, warning = F, message = F}
 
@@
 
-effect_plot(mods12, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
-effect_plot(mods12, best_win, flanker_c) # Words in Noise * Inhibitory Control
-effect_plot(mods12, pattern_c, best_win, num = 4) # Processing Speed * Words in Noise Threshold
-effect_plot(mods12, best_win, pattern_c, num = 4)
-effect_plot(mods12, card_sort_c, best_win, num = 5) # Cognitive Flexibility * Words in Noise Threshold
-effect_plot(mods12, flanker_c, vocab_c, num = 5) # Inhibitory Control * Receptive Vocabulary
-effect_plot(mods12, vocab_c, flanker_c, num = 5) # Receptive Vocabulary * Inhibitory Control
+effect_plot(mods12, flanker_c, best_win, num = 4) # Inhibitory Control * Words in Noise Threshold
+effect_plot(mods12, best_win, flanker_c, num = 4) # Words in Noise * Inhibitory Control
+effect_plot(mods12, pattern_c, best_win) # Processing Speed * Words in Noise Threshold
+effect_plot(mods12, best_win, pattern_c) # Words in Noise Threshold * Processing Speed
 
@@
 ```
+## Interaction Effects
 
-The interaction effects for the intelligibility improvement models for PDM10 are plotted below.
-
--   The interaction between cognitive flexibility and receptive vocabulary indicates that cognitive flexibility had a positive effect on improvement for listeners with higher vocabulary knowledge, but minimal effect for listeners with lower vocabulary knowledge
--   The interaction effect between inhibitory control and processing speed indicates that processing speed has a negative effect on intelligibility improvement for listeners with mid-range inhibitory control.
-However, processing speed has minimal effect on improvement when listeners have lower or higher inhibitory control scores.***
+-   The interaction between cognitive flexibility and receptive vocabulary indicates that listeners with high cognitive flexibility  and high vocabulary knowledge had greater intelligibility improvement for PDM10.
+However, higher cognitive flexibility tends to have a negative effect on intelligibility improvement for PDM10 for listeners with low vocabulary knowledge.
+***
+-   The interaction effect between inhibitory control and processing speed indicates that increased processing speed has a negative effect on intelligibility improvement for listeners with higher inhibitory control.
+However, processing speed has minimal effect on improvement when listeners have lower inhibitory control.
+***
 -   Receptive vocabulary has a positive effect on intelligibility improvement.
 -   Inhibitory control has a negative effect on intelligibility improvement.
--   The interaction between inhibitory control and words in noise threshold indicates a positive effect of inhibitory control for listeners with low words in noise thresholds but little to no effect for listeners with elevated hearing thresholds (a potential negative effect)
+-   The interaction between inhibitory control and words in noise threshold indicates that inhibitory control had a positive effect on intelligibility improvement for listeners with low words in noise thresholds.
+However, inhibitory control had a minimal, and potentially negative, effect on intelligibility improvement for listeners with elevated thresholds.
+***
 
-```{r, warning = F, message = F}
+```{r, eval = F, warning = F, message = F}
 
@@
 effect_plot(mods22, flanker_c, best_win, num = 4) # Inhibitory Control * Words in Noise Threshold
+effect_plot(mods22, best_win, flanker_c, num = 4) # Words in Noise Threshold * Inhibitory Control
 
@@
 ggsave("Plots/Change_mods.png", plot = last_plot(), width = 8, height = 10, units = "in")
+
+p12 + p22
+ggsave("Plots/Change_mods_wide.png", plot = last_plot(), width = 15, height = 5, units = "in")
 

### 2024-04-16 Manuscript Analyses/manuscript_analysis.Rmd
updated figures and tables

@@
 
+demo <- cor_df %>%
+  dplyr::select(id, speaker) %>%
+  dplyr::left_join(demo, by = "id")
+
 ```
@@
 
-A total of 60 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
+A total of 59 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
 
-```{r}
+```{r, warning = F, message = F}
 
@@
   dplyr::select(-id) %>%
-  tbl_summary(type = list(age ~ "continuous",
+  tbl_summary(by = speaker,
+              type = list(age ~ "continuous",
                           gender ~ "categorical",
@@
               digits = list(everything() ~ c(2))) %>%
+  add_overall() %>%
   as_gt()
@@
 # Customize colors for figures
-library(LaCroixColoR) #remotes::install_github("johannesbjork/LaCroixColoR")
+library(LaCroixColoR) # remotes::install_github("johannesbjork/LaCroixColoR")
 
-my_pal <- c("#782F40", "#B89751")
+my_pal <- c("#62A87C", "#313B72")
 
@@
       y = pwc,
-      group = id,
-      color = speaker) +
+      group = id) +
   geom_line(alpha = 0.3) +
   geom_point(alpha = 0.3) +
-  stat_summary(aes(group = speaker),
+  stat_summary(aes(group = speaker, color = speaker),
                fun.y = mean, geom = "line", linewidth = 2) +
@@
 
-## Interaction Effects
+#### Interaction Effects
 
@@
 However, inhibitory control had minimal effects for listeners with elevated hearing thresholds.
--   The interaction between processing speed and words in noise threshold indicate that greater processing speed has a negative effect on intelligibility improvement for listeners with higher hearing thresholds.
+-   The interaction between processing speed and words in noise threshold indicate that greater processing speed has a postive effect on intelligibility improvement for listeners with lower hearing thresholds.
+However, it likely has a negative effect on intelligibility improvement for listeners with higher hearing thresholds.
 ***
@@
 ```
-## Interaction Effects
+#### Interaction Effects
 
@@
 However, higher cognitive flexibility tends to have a negative effect on intelligibility improvement for PDM10 for listeners with low vocabulary knowledge.
-***
 -   The interaction effect between inhibitory control and processing speed indicates that increased processing speed has a negative effect on intelligibility improvement for listeners with higher inhibitory control.

### 2024-05-01 Manuscript Analyses/manuscript_analysis.Rmd
minor figure edits

@@
 
-# Customize colors for figures
-library(LaCroixColoR) # remotes::install_github("johannesbjork/LaCroixColoR")
-
 my_pal <- c("#62A87C", "#313B72")
@@
 pl_int %>%
+  dplyr::mutate(speaker = factor(speaker, levels = c("AM1", "PDM10"),
+                                 labels = c("Ataxic","PD"))) %>%
   ggplot() +
@@
 # Customize plot colors
+library(LaCroixColoR)
 my_pal <- lacroix_palette("PeachPear", n = 15, type = "continuous")
@@
     insig = "blank",
-    title = "Parkinson's Disease", 
+    title = "PD", 
     legend.title = "Correlation"

### 2024-05-01 Manuscript Analyses/manuscript_analysis.Rmd
added interpretations for AM1 intelligibility improvement model

@@
 ***
+- The interaction between cognitive flexibility and words in noise threshold indicate that greater cognitive flexibility has a positive effect on intelligibility improvement for listeners with higher (i.e.
+worse) words in noise hearing thresholds.
+However, it did not have much of an effect for listeners with lower WIN thresholds.
+- The interaction between receptive vocabulary and inhibiotry control indicate that greater receptive vocabulary has a positive effect on intelligibility improvement for listeners with very low and very high inhibitory control (i.e.
+higher receptive vocabulary had a compensatory effect for listeners with low inhibitory control and an additive effect for listeners with very high inhibitory control).
+However, receptive vocabulary appears to have a negative effect for listeners with around average inhibitory control (i.e.
+higher receptive vocabulary was associated with less intelligibility improvement for listeners with mid-range inhibitory control skills).
 
@@
 effect_plot(mods12, best_win, pattern_c) # Words in Noise Threshold * Processing Speed
+effect_plot(mods12, best_win, card_sort_c) # Words in Noise Threshold * Cognitive Flexibility
+effect_plot(mods12, card_sort_c, best_win) # Cognitive Flexibility * Words in Noise Threshold
+effect_plot(mods12, flanker_c, vocab_c, num = 4) # Inhibitory Control * Receptive Vocabulary
+effect_plot(mods12, vocab_c, flanker_c, num = 4) # Receptive Vocabulary * Inhibitory Control
 

### 2024-05-03 Manuscript Analyses/manuscript_analysis.Rmd
evaluated main effect of inhibitory control on int intel

@@
 effect_plot(mods2, card_sort_c, list_sort_c) # Cognitive Flexibility * Working Memory
+effect_plot(mods2, flanker_c, int = F) # Inhibitory Control
 

### 2024-09-06 Manuscript Analyses/manuscript_analysis.Rmd
updated tables

@@
 
-All data processing and analyses were conducted using R Version 4.3.2.
+All data processing and analyses were conducted using R Version 4.4.1
 
@@
 
+## Younger adult df
+young_adult <- rio::import("cleaned_scored.csv") |>
+  dplyr::select(-group_number)
+
 ```
@@
 
-# Removing Participant 323 from the dataset (missing demographic and cognitive data)
+# Removing Participant 323 and 332 from the dataset (missing demographic and cognitive data)
 
 data <- data %>%
-  dplyr::filter(id != 323)
+  dplyr::filter(id != 323 & id != 332)
 
 demo <- demo %>%
-  dplyr::filter(id != 323)
+  dplyr::filter(id != 323 & id != 332)
 
@@
   gt::gtsave("Tables/means_tabel.html")
+
+```
+
+### Comparing Younger vs. Older Adults
+
+#### Age-Corrected
+
+The younger adult data comes from https://osf.io/y32qc/
+
+```{r}
+
+older_adult <- pl_int |>
+  dplyr::filter(type == "pretest") |>
+  dplyr::select(id, ends_with("_c"), ends_with("_u"), best_win) |>
+  dplyr::select(-c(fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u)) |>
+  dplyr::rename(win = best_win) |>
+  dplyr::mutate(group = "old") |>
+  dplyr::filter()
+
+young_adult <- young_adult |>
+  dplyr::select(-c(age_in_years, win_l, win_r, fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u))
+
+compare_df <- rbind(older_adult, young_adult)
+
+compare_table_c <- compare_df %>%
+  dplyr::select(id, ends_with("_c"), win, group) %>% 
+  dplyr::rename(
+    `Working Memory` = list_sort_c,
+    `Inhibitory Control` = flanker_c,
+    `Cognitive Flexibility` = card_sort_c,
+    `Receptive Vocabulary` = vocab_c,
+    `Processing Speed` = pattern_c,
+    `Words in Noise Threshold` = win
+  ) %>%
+  select(-id) %>% 
+  tbl_summary(
+    by = group,
+    statistic = list(all_continuous() ~ "{mean} ({sd})"),
+    missing = "no",
+    digits = list(everything() ~ c(2))
+  ) %>% 
+  add_p() %>%
+  as_gt()
+
+compare_table_c
+
+```
+
+#### Uncorrected Scores
+
+```{r}
+
+compare_table_u <- compare_df %>%
+  dplyr::select(id, ends_with("_u"), win, group) %>% 
+  dplyr::rename(
+    `Working Memory` = list_sort_u,
+    `Inhibitory Control` = flanker_u,
+    `Cognitive Flexibility` = card_sort_u,
+    `Receptive Vocabulary` = vocab_u,
+    `Processing Speed` = pattern_u,
+    `Words in Noise Threshold` = win
+  ) %>%
+  select(-id) %>% 
+  tbl_summary(
+    by = group,
+    statistic = list(all_continuous() ~ "{mean} ({sd})"),
+    missing = "no",
+    digits = list(everything() ~ c(2))
+  ) %>% 
+  add_p() %>%
+  as_gt()
+
+compare_table_u
 

### 2024-09-06 Manuscript Analyses/manuscript_analysis.Rmd

@@
   ) %>%
-  group_by(id, speaker) %>% 
-  summarize(across(everything(), first)) %>% 
-  ungroup() %>% 
   select(-id) %>% 
@@
   ) %>%
+  dplyr::mutate(group = factor(group, levels = c("young", "old"))) %>%
   select(-id) %>% 
@@
   ) %>% 
-  add_p() %>%
-  as_gt()
+  add_p()
 
@@
   ) %>% 
-  add_p() %>%
-  as_gt()
+  add_p()
 
 compare_table_u
+
+```
+
+```{r, eval = F}
+
+tbl_merge(tbls = list(compare_table_u, compare_table_c),
+          tab_spanner = c("***Uncorrected Standardized Scores***", "***Age-Corrected Standardized Scores***")) |>
+  as_gt() |>
+  gt::gtsave("Tables/compare_table.html")
+
+```
+
+```{r, echo = F}
+
+rm(young_adult, older_adult, compare_table_c, compare_table_u, compare_df)
 
@@
 
-The plot below shows only the significant correlations in the matrix above for AM1.
-
-```{r, warning = F, message = F}
-
-cor_df %>%
-  dplyr::filter(speaker == "AM1") %>%
-  dplyr::select(!c(id, speaker, fluid_cog_c, pic_seq_c, posttest)) %>%
-  dplyr::rename(
-    `Working Memory` = list_sort_c,
-    `Inhibitory Control` = flanker_c,
-    `Cognitive Flexibility` = card_sort_c,
-    `Receptive Vocabulary` = vocab_c,
-    `Processing Speed` = pattern_c,
-    `Words in Noise Threshold` = best_win
-  ) %>%
-  dplyr::rename_all(snakecase::to_title_case) %>%
-  cor(use = "pairwise.complete.obs") %>%
-  ggcorrplot(
-    type = "lower",
-    outline.col = "white",
-    colors = c(my_pal[1], "white", my_pal[15]),
-    lab = TRUE,
-    p.mat = cor_pmat(.),
-    sig.level = 0.05,
-    insig = "blank",
-    title = "Ataxic", 
-    legend.title = "Correlation"
-  )
-
-```
-
 ### PDM10
@@
 PDM10_cor
-
-```
-
-The plot below only shows the significant correlations for PDM10.
-
-```{r}
-
-cor_df %>%
-  dplyr::filter(speaker == "PDM10") %>%
-  dplyr::select(!c(id, speaker, fluid_cog_c, pic_seq_c, posttest)) %>%
-  dplyr::rename(
-    `Working Memory` = list_sort_c,
-    `Inhibitory Control` = flanker_c,
-    `Cognitive Flexibility` = card_sort_c,
-    `Receptive Vocabulary` = vocab_c,
-    `Processing Speed` = pattern_c,
-    `Words in Noise Threshold` = best_win
-  ) %>%
-  dplyr::rename_all(snakecase::to_title_case) %>%
-  cor(use = "pairwise.complete.obs") %>%
-  ggcorrplot(
-    type = "lower",
-    outline.col = "white",
-    colors = c(my_pal[1], "white", my_pal[15]),
-    lab = TRUE,
-    p.mat = cor_pmat(.),
-    insig = "blank",
-    sig.level = 0.05,
-    title = "Parkinson's Disease", 
-    legend.title = "Correlation"
-  )
 

### 2024-09-09 Manuscript Analyses/manuscript_analysis.Rmd
added overall age descriptives

@@
 
+We had to remove two participants from this analysis since we do not have any cognitive or hearing data from them.
+However, the mean age and range for all 60 participants we collected are below.(Note: one of the people we dropped also didn't have their age recorded.
+Therefore the M/SD below )
+
+```{r, warning = F, message - F}
+
+demo %>%
+  dplyr::select(-c(id, gender, race, ethnicity)) %>%
+  tbl_summary(type = list(age ~ "continuous"),
+              statistic = list(all_continuous() ~ "{mean} ({sd});{min}-{max})"),
+              missing = "no",
+              digits = list(everything() ~ c(2)))
+```
+
 First, pretest and posttest intelligibility was calculated as a percent words correct (pwc) score for each listener.
@@
 demo <- demo %>%
-  dplyr::filter(id != 323 & id != 332)
+  dplyr::filter(id != 323 & id != 332 )
 
@@
 
-A total of 59 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
+A total of 58 older adult listeners participated in the study (excluding the two listeners we had to remove). The overall demographic information for the 58 participants are in the table below.
 

### 2024-12-13 Manuscript Analyses/data_processing_updated.R
fixed coding error in data prep

@@ -1,7 +1,7 @@
 # Data Preprocessing
 
 # Author: Micah E. Hirsch (mhirsch@fsu.edu)
-# Date: 12/7/2023
+# Date: 12/13/2024
 
 # R Version: 4.3.2
 # Purpose: To prepare data for analysis
@@ -18,7 +18,7 @@ library(lubridate) #install.packages("lubridate")
 
 # Set Working Directory
 
-setwd("~/Documents/Github Repositories/Older Adult PL Study Analysis/Raw Data")
+setwd("~/Documents/Github/Older Adult PL Study Analysis/Raw Data")
 
 # Specifying paths for where listener data is located
 file_path <- list.dirs(path = "./Participant Data", full.names = T, recursive = F)
@@ -108,13 +108,18 @@ transcriptions <- transcriptions %>%
 
 targets <- rio::import_list("Stimuli List/Stimuli Testing Sets.xlsx", 
                             which = c("Pretest", "Posttest"), rbind = T, rbind_label = "Type") %>%
-  rename_all(., .funs = tolower)
+  rename_all(., .funs = tolower) %>%
+  dplyr::mutate(target = tolower(target),
+                target = trimws(target, "both"),
+                target_number = str_count(target, "\\S+"))
 
 transcriptions_fixed <- transcriptions %>%
-  dplyr::rename(target2 = target) %>%
+  dplyr::rename(target2 = target,
+                target_number2 = target_number) %>%
   dplyr::left_join(targets, by = "code") %>%
-  mutate(target = dplyr::if_else(speaker %in%  "PDM10", target2, target)) %>% 
-  select(-c(target2, type.y)) %>%
+  mutate(target = dplyr::if_else(speaker %in%  "PDM10", target2, target),
+         target_number = dplyr::if_else(speaker %in% "PDM10", target_number2, target_number)) %>% 
+  select(-c(target2, target_number2, type.y)) %>%
   dplyr::rename(type = type.x) %>%
   dplyr::relocate(target, .before = target_number)
 
@@ -253,7 +258,7 @@ cleaned_data <- cleaned_data %>%
 rm(cog, cog_subtests, cog1, corrected, uncorrected, win, words_in_noise, i, new_names)
 
 # Export 
-setwd("~/Documents/Github Repositories/Older Adult PL Study Analysis/Manuscript Analyses")
+setwd("~/Documents/Github/Older Adult PL Study Analysis/Manuscript Analyses")
 
[…]

### 2024-12-13 Manuscript Analyses/manuscript_analysis.Rmd
rerendered analysis report

--- 2024-09-06 Manuscript Analyses/manuscript_analysis.Rmd
@@
 
-All data processing and analyses were conducted using R Version 4.4.1
+All data processing and analyses were conducted using R Version 4.3.2.
 
@@
 data <- rio::import("cleaned_data.csv")
-
-## Younger adult df
-young_adult <- rio::import("cleaned_scored.csv") |>
-  dplyr::select(-group_number)
 
@@
 
-A total of 59 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
+A total of 58 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
 
@@
 
-### Comparing Younger vs. Older Adults
-
-#### Age-Corrected
-
-The younger adult data comes from https://osf.io/y32qc/
-
-```{r}
-
-older_adult <- pl_int |>
-  dplyr::filter(type == "pretest") |>
-  dplyr::select(id, ends_with("_c"), ends_with("_u"), best_win) |>
-  dplyr::select(-c(fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u)) |>
-  dplyr::rename(win = best_win) |>
-  dplyr::mutate(group = "old") |>
-  dplyr::filter()
-
-young_adult <- young_adult |>
-  dplyr::select(-c(age_in_years, win_l, win_r, fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u))
-
-compare_df <- rbind(older_adult, young_adult)
-
-compare_table_c <- compare_df %>%
-  dplyr::select(id, ends_with("_c"), win, group) %>% 
-  dplyr::rename(
-    `Working Memory` = list_sort_c,
-    `Inhibitory Control` = flanker_c,
-    `Cognitive Flexibility` = card_sort_c,
-    `Receptive Vocabulary` = vocab_c,
-    `Processing Speed` = pattern_c,
-    `Words in Noise Threshold` = win
-  ) %>%
-  select(-id) %>% 
-  tbl_summary(
-    by = group,
-    statistic = list(all_continuous() ~ "{mean} ({sd})"),
-    missing = "no",
-    digits = list(everything() ~ c(2))
-  ) %>% 
-  add_p() %>%
-  as_gt()
-
-compare_table_c
-
-```
-
-#### Uncorrected Scores
-
-```{r}
-
-compare_table_u <- compare_df %>%
-  dplyr::select(id, ends_with("_u"), win, group) %>% 
-  dplyr::rename(
-    `Working Memory` = list_sort_u,
-    `Inhibitory Control` = flanker_u,
-    `Cognitive Flexibility` = card_sort_u,
-    `Receptive Vocabulary` = vocab_u,
-    `Processing Speed` = pattern_u,
-    `Words in Noise Threshold` = win
-  ) %>%
-  select(-id) %>% 
-  tbl_summary(
-    by = group,
-    statistic = list(all_continuous() ~ "{mean} ({sd})"),
-    missing = "no",
-    digits = list(everything() ~ c(2))
-  ) %>% 
-  add_p() %>%
-  as_gt()
-
-compare_table_u
-
-```
-
 ## Intelligibility
@@
 However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10.
-A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p \< .001, d = 1.01).
+A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,31) = 101.83, p \< .001, d = 1.05).
 

### 2024-12-13 Manuscript Analyses/manuscript_analysis.Rmd

--- 2024-09-09 Manuscript Analyses/manuscript_analysis.Rmd
@@
 demo <- demo %>%
-  dplyr::filter(id != 323 & id != 332 )
+  dplyr::filter(id != 323 & id != 332)
 
@@
 
-A total of 58 older adult listeners participated in the study (excluding the two listeners we had to remove). The overall demographic information for the 58 participants are in the table below.
+A total of 58 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
 
